---
title: "Seamless Phase IIB/C Simulation Study Design"
author: "Suzanne Dufault"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../graphs/exploratory/")
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
library(simsurv)
```

```{r initial-data-setup}
# Call in model being used as "truth"
files <- file.info(list.files("~/OneDrive - University of California, San Francisco/Research/phase2b-simstudy/data/bayes-generated/", full.names = T))
file_interest <- files[stringr::str_detect(rownames(files), "remox-lmm-short_lower-detection-25"),]
load(rownames(file_interest)[which.max(file_interest$mtime)])
rm(file_interest,files)

# Pull out coefficients
s <- summary(fit.cens.ld.25)
betas <- c(s$fixed$Estimate)[1:2] # (just the intercept and control group slope for now)

# Pull out individual-level SD
sd_id <- s$random$trial_no$Estimate[1]

# Pull out random slope SD
sd_slope <- s$random$trial_no$Estimate[2] 

# Pull out randome effects correlation
rho <- s$random$trial_no$Estimate[3] 

# Pull out residual SD
sd_randomnoise <- s$spec_pars$Estimate[1]

# SET SEED
lod <- 25 # limit of detection for log10(TTP)
betas.log10ttp <- c(betas, # intercept, slope for control
                    betas[2]*seq(0.1,0.4,by = 0.1)) # 1st-4th regimens
k <- 5 # number of regimens
d <- c(8,10,12,14,16)  # durations per regimen (weeks) -- fixed for now, except for in control arm
enroll.time.weeks <- 75 # the trial time in weeks (before first interim analysis, 16 weeks)
nkd <- 30 # number of participants per regimen and duration at end of study


cormat <- matrix(c(sd_id, # sd random intercept
                   rho, rho, #rho
                   sd_slope), # sd random slope
                 2,2)
covmat <- lme4::sdcor2cov(cormat) # covariance matrix
umat <- MASS::mvrnorm(nkd*k*length(d), 
                      mu = c(0,0),
                      covmat,
                      empirical = TRUE)

Z <- data.frame(umat) %>% 
  rename("random.intercept" = 1, "random.slope" = 2) %>% 
  mutate(patient.id = paste0("id", row_number())) %>% 
  dplyr::select(patient.id, everything())

# Set up fixed effects
df_temp <- data.frame(
    # Generate the regimen ID
    regimen = rep(1:k, times = nkd*length(d)),
    # Generate duration ID
    duration = rep(d, each = nkd*k)) %>% 
  mutate(
    # Sample enrollment time 
    enroll.day = sample(1:(7*(nkd*k*length(d))/10), size = nkd*k*length(d), replace = TRUE)) %>%
  arrange(enroll.day) %>%
  # Control regimen is ONLY a 6-month regimen
  mutate(duration = ifelse(regimen == 1, 26, duration),
         patient.id = paste0("id", row_number())) 
  
```


# Design {.tabset}

## Notation 

<!-- | Symbol | Definition | -->
<!-- |:------:|:-----------| -->
<!-- | $X$    | R.V. regimen, $x = 1,\ldots,K$ | -->
<!-- | $Y$    | R.V. log10(TTP), $y \in [\log_{10}1, \log_{10}\text{LOD})$ | -->
<!-- | $D$    | R.V. duration (weeks), $d = \{8,10,12,14,16,24\}$ | -->
<!-- | $T$ | continuous r.v. trial time (weeks) $\tau \in [0, T_{\tau}]$ | -->
<!-- | $T_t$ | continuous r.v. patient time (weeks) $t \in [0,52]$ | -->

There are two distinct timelines that we will need to be aware of for simulating: 

1. Trial time: $\tau = 0, \ldots, T_{\tau}$ weeks
    + The interim and final analyses are scheduled according to trial time.
    + Time of relapse occurrence with respect to trial time will be necessary for interim and final analyses.
2. Patient time: $t = 0,\ldots T_t = 365$ days.
    + For each patient, patient time starts at baseline and counts forward their weeks since randomization. Each patient is followed for a total of 52 weeks. Events after 52 weeks of patient follow-up are censored.
    + Patient time is particularly useful for the log10(TTP) analyses from the first *56* days of observation after randomization.
    + Patient time is also useful for determining a patient's "at risk" status for relapse, since relapse can only occur once treatment is complete. 
  

Hypothetical Data:

| Patient ID | Date Enrollment | Regimen | Duration (days) | Days since randomization | TTP | log10(TTP) | Relapse? | Date of Relapse |
|:-----------|:----------------|:--------|:---------|:------------------------|:---|:---|:---|:---|
| id001 | 2022-01-01 | HRZE | 24 |  0 | 10 | 1.00 | No | NA |
| id001 | 2022-01-01 | HRZE | 24 |  1 | 13 | `r round(log10(13),2)` | No | NA |
| id001 | 2022-01-01 | HRZE | 24 |  1.85 | 14 | `r round(log10(14),2)` | No | NA |
| id001 | 2022-01-01 | HRZE | 24 | $\vdots$ | $\vdots$ | $\vdots$ | No | NA |
| id002 | 2022-01-02 | TRT1 | 8 |  0 | 11 | `r round(log10(11),2)` | Yes | 2022-05-03 |
| id002 | 2022-01-02 | TRT1 | 8 |  0.95 | 12.7 | `r round(log10(12.7),2)` | Yes | 2022-05-03 |
| id002 | 2022-01-02 | TRT1 | 8 |  2.2 | 14.8 | `r round(log10(14.8),2)` | Yes | 2022-05-03 |
| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |  $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |

Hypothetical Data (transformed to our time scales):

| Patient ID | Day of Enrollment ($\tau_0$) | Regimen | Duration (days) | Days since randomization ($t$) | TTP | log10(TTP) | Relapse? | Day of Relapse ($\tau_y$) |
|:-----------|:----------------|:--------|:---------|:------------------------|:---|:---|:---|:---|
| id001 | 0 | HRZE | 168 |  0 | 10 | 1.00 | No | NA |
| id001 | 0 | HRZE | 168 |  7 | 13 | `r round(log10(13),2)` | No | NA |
| id001 | 0 | HRZE | 168 |  13 | 14 | `r round(log10(14),2)` | No | NA |
| id001 | 0 | HRZE | 168 | $\vdots$ | $\vdots$ | $\vdots$ | No | NA |
| id002 | 1 | TRT1 | 56 |  0 | 11 | `r round(log10(11),2)` | Yes | 122 |
| id002 | 1 | TRT1 | 56 |  6 | 12.7 | `r round(log10(12.7),2)` | Yes | 122 |
| id002 | 1 | TRT1 | 56 |  16 | 14.8 | `r round(log10(14.8),2)` | Yes | 122 |
| $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |  $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ | $\vdots$ |


We effectively need to simulate the following:

1. Random enrollment date $\tau_{0i}$ for each participant $\tau_{0i} \in [0,T_{\tau}]$. This will affect who is included in interim and final analyses.
    + Individuals will be concurrently randomized to regimens and durations.
    + Assume a random enrollment rate of 10 participants per week.
2. log10(TTP) as a function of participant days since randomization ($t \in [0,56]$) and regimen.   
3. Relapse as a function of regimen and duration (assuming monotonic relationship) for $t \in [57, 365]$.

For now, we can start with a single wave of regimens. Can later incorporate multiple regimen waves.


## log10(TTP)

\[Y_{ij} |\beta_{0i}, \beta_{1i}, \beta_2,\ldots,\beta_K,\sigma \sim N(\mu_{ij},\sigma^2)\]
\[\beta_{0i}|\beta_0,\sigma_0 \sim N(\beta_0,\sigma_0^2)\]
\[\beta_{1i}|\beta_1,\sigma_1 \sim N(\beta_1,\sigma_1^2)\]
\[\beta_0 \sim N()\]
\[\beta_1 \sim N()\]
\[\beta_{K} \sim N(p_K\times\beta_1,\sigma_K^2)\]


\[\log_{10}(TTP_{ij}) = \beta_{0i} + \beta_{1i}Z_j + \beta_2Z_j\cdot\mathbb{I}(X_i = 2) + \ldots + \beta_KZ_j\cdot I(X_i =K) + e_{ij}\]

where $Z$ denotes days since randomization for measurement $j = 1,\ldots,9$ and $X$ denotes assigned regimen, $X = 1,\ldots, K$.

## Survival {.tabset .tabset-pills}

To simulate censored survival data, we must specify two survival distributions:

1. Uncensored survival times observed under no censoring
2. Censoring mechanism
    + For now, we will assume there is no loss to follow-up. Therefore, the only non-informative censoring that occurs is administrative end of follow-up.

For now, each patient enters the risk set for adverse survival outcomes *after* they have completed treatment. **We are assuming all individuals finish treatment.** Each individual is followed for 52 weeks post-randomization. Therefore, their maximum survival follow-up time is: 52 weeks - duration of intervention (weeks).

<!-- ### Exponential Hazards Model -->

<!-- Let's assume that $t\sim\text{Exp}(\lambda)$, where $\lambda = h(t|X)$ and $t$ is week since end of treatment. -->

<!-- Then the hazard function can be written as: -->

<!-- \[\begin{align} -->
<!-- \log[h(t|X)] &= \log(h_0) + \beta_1X_1 + \ldots + \beta_pX_p \\ -->
<!-- \log[h(t|X)] &= \beta_0 + \beta_1X_1 + \ldots + \beta_pX_p  -->
<!-- \end{align}\] -->

<!-- In our setting, we will consider the duration and the regimen as the covariates of interest for the linear predictor. As such, we will simulate from the following log-hazard function: -->

<!-- \[\log[h(t|x)] = \beta_0 + \beta_1\times duration + \beta_2 \times \mathbb{I}(\text{regimen} = 2) + \ldots + \beta_K \times \mathbb{I}(\text{regimen = K})\] -->

<!-- where: -->

<!-- + $\beta_0$ is the log-hazard in the control regimen with a 6-month duration -->
<!--   + For now: $\beta_0 = \log(0.03)$ -->
<!-- + $\beta_1$ is the change in log-hazard (i.e., log HR) for each week decrease in duration of regimen -->
<!--   + Assume: monotonic, longer duration decreases hazard of relapse -->
<!--   + $\beta_1 = \log(0.9)$ -->
<!-- + $\beta_k, k = 2,...,K$ is the change in log-hazard for "novel" regimen $k$ compared to the control  -->
<!--   + Note: control is always a 6-month regimen -->
<!--   + For now, assume $\beta_k = \log(2), k = 2,...,K$ -->

<!-- #### Parameterizing the model -->

<!-- ```{r exponential-function, eval = FALSE} -->
<!-- exponential_function <- function(lambda, surv.prop, t){ -->
<!--   exp(-lambda*t) - surv.prop -->
<!-- } -->

<!-- surv.prop = 0.96 -->
<!-- t = 12 -->
<!-- uniroot(exponential_function, -->
<!--         interval = c(0,5), -->
<!--         surv.prop = surv.prop, -->
<!--         t = t) -->
<!-- ``` -->

### Weibull Proportional Hazards Model

We know that the hazard isn't constant over time, but is instead highest right after treatment ends and then decreases over time. To parameterize this model, we'll assume that patient time $T_t \sim \text{Weibull}(\lambda,p)$.

#### Parameterizing the model

The Weibull model has two unknown parameters, the rate $\lambda$ and shape $p$. To set up our simulations, we will fix the expected survival rate at 26 weeks post-treatment (i.e., corresponding to 52 weeks post-randomization) and then back solve for $\lambda$. We will also fix $p$ such that about 75% of events have occurred within 3 months (13 weeks).

The survival and hazard functions:

\[\begin{align}
S(t) &= e^{-\lambda t^p} \\
h(t) &= \lambda pt^{p-1}
\end{align}\]

We'll consider the following:

+ $S(26) = \{0.97, 0.95, 0.90\}$

```{r weibull-function}
weibull_function <- function(lambda, p, surv.prop, t){
  exp(-lambda*t^p) - surv.prop
}

p = seq(0.4:0.9, by = 0.025)
surv.prop = c(0.97, 0.95, 0.9)
t = 26

df_params <- expand.grid(p, surv.prop) %>% 
  rename("p" = 1, "surv.prop" = 2) %>% 
  mutate(t = t)

lambda <- apply(df_params, 1, function(x){
  output <- uniroot(weibull_function,
          interval = c(0,10),
          p = x[1],
          surv.prop = x[2],
          t = x[3])
  output$root
})
```

We'll further specify that 75% of failure events occur within the first 13 weeks ($\approx 3$ months). For example, when $S(26) = 0.97, F(26) = 1 - S(26) = 0.03$:

\[\begin{align}
F(13) &= F(26)\times0.75 \\
 &= 0.03\times 0.75\\
 &= 0.0225 \\
S(13) &= 1-F(13) \\
 &= 0.9775
\end{align}\]

For each of our specified survival/failure rates, setting $p = 0.425$ allows approximately 75% of failure to occur in the first 13 weeks.

<!-- > (Table 2)[https://www.nejm.org/doi/full/10.1056/NEJMoa2033400]. 3.3% of participants in the HRZE group had an unfavorable outcome related to tuberculosis at 12 months post-randomization.  -->

```{r include = FALSE}

# This is how we've determined p = 0.425 is "optimal" for our purposes

out1 <- bind_cols(df_params, lambda = lambda) 
s13 <- apply(out1, 1,  function(x){uniroot(weibull_function, 
                                lambda = x[4], 
                                p = x[1], 
                                t = 13, 
                                interval = c(0,1))$root})

target.s13 <- data.frame(surv.prop = c(0.97, 0.95, 0.9)) %>% 
  mutate(s13.target = 1 - (1 - surv.prop)*0.75)

out1 %>%
  bind_cols(s13 = s13) %>% 
  left_join(target.s13) %>% 
  dplyr::select(`Time (t)` = t, 
                `S(26)` = surv.prop,
                p,
                lambda,
                `S*(13)` = s13,
                `Target S(13)` = s13.target) %>% 
  ggplot(aes(x = p, y = `S*(13)`, col = as.factor(`S(26)`))) + 
  geom_line() + 
  geom_hline(yintercept = target.s13$s13.target)

out1 %>%
  bind_cols(s13 = s13) %>% 
  left_join(target.s13) %>% 
  dplyr::select(`Time (t)` = t, 
                `S(26)` = surv.prop,
                p,
                lambda,
                `S*(13)` = s13,
                `Target S(13)` = s13.target) %>% 
  ungroup() %>% 
  kable(digits = 4,
        caption = "For HRZE based on 12 months post-randomization, these are the estimated weekly hazard rates (lambda) based on the fixed values of t, p, S(t).") %>%
  kable_styling() %>%
  collapse_rows()
```


#### Adding in covariates

Next, we re-parameterize $\lambda$ such that it depends on a set of covariates $X$, (e.g., $\lambda = \exp(X\beta)$) we can rewrite the hazard function as follows:

\[\begin{align}
h(t|X) &= \exp(X\beta)\times pt^{p-1}\\
\log[h(t|X)]&= \log(p t^{p-1}) + \beta_0 + \beta_1X_1 + \ldots + \beta_pX_p 
\end{align}\]

In our setting, we will consider the duration and the regimen as the covariates of interest for the linear predictor. Our reference group will be regimen 1 (the control regimen) which has a duration of 26 weeks. As such, we will simulate from the following log-hazard function:

\[\begin{align}
\log[h(t|\text{regimen}, g(d))] &= \log(p t^{p-1}) + \beta_0 + \beta_1 \times \mathbb{I}(\text{regimen} = 2) + \cdots + \beta_{K-1} \times \mathbb{I}(\text{regimen = K}) \\
& \hspace{1em}+ \beta_K\mathbb{I}(\text{regimen} = 2)\times g(d) + \cdots + \beta_{2(K-1)}\mathbb{I}(\text{regimen} = K)\times g(d)
\end{align}\]

where:

+ $\log(p t^{p-1}) + \beta_0$ is the log-hazard over time in the control regimen with a 6-month duration
  + $\beta_0 = \log\lambda$ from the previous table. 
  + $p$ is the corresponding $p$ from the previous table
+ $\beta_k, k = 2,...,K-1$ is the change in log-hazard for "novel" regimen $k$ compared to the control IF durations were the same (which they are not)
  + Note: control is always a 6-month regimen
+ $\beta_k, k = K,...,2\times(K-1)$ is an interaction term allowing the log-hazard for the novel regimen to depend on the length of treatment duration $d$
  + Either directly $g(x) = x$, or could *consider as a difference in duration relative to control $g(x) = 26-x$*.
  + For now, assume "linearity". For each week increase in duration, the log-hazard for novel regimen $k$ changes by $\beta_k, k = K,\ldots, 2(K-1)$. 
  
For now, we will assume $\beta_K,\ldots,\beta_{2(K-1)} = \beta_K^*$, meaning that the effect of changing the duration of the regimen on the hazard is consistent across all regimens. The parametric model we are simulating from now simplifies to:

\[\begin{align}
\log[h(t|\text{regimen}, g(d))] &= \log(p t^{p-1}) + \beta_0 + \beta_1 \times \mathbb{I}(\text{regimen} = 2) + \cdots + \beta_{K-1} \times \mathbb{I}(\text{regimen = K}) \\
& \hspace{1em}+ \beta_K\times g(d)
\end{align}\]

Now, we specify the regimen characteristics. Let $S_k(t)$ denote the survival rate for arm $k$ at time $t$.

| Setting | Regimen | Characteristics | Questions of Interest |
|:-------:|:-------:|:----------------|:----------------------|
| 1 | 2 | suboptimal, $S_2(52-16) = S_1(26)\times0.95$ | Are we able to identify the best regimen? How often do we discard the best regimen/carry forward the worst regimen at interim?|
| | 3 | minimal, $S_3(52-12) = S_1(26)$ | |
| | 4 | minimal, $S_4(52-12) = S_1(26)$ | |
| | 5 | desirable, $S_5(52-8) = S_1(26)$ | |
| | | | |
| 2 | 2 | desirable, $S_2(52-8) = S_1(26)$ | What is the risk of having the slope decision-making step when all are good?|
| | 3 | desirable, $S_3(52-8) = S_1(26)$ | |
| | 4 | desirable, $S_4(52-8) = S_1(26)$ | |
| | 5 | desirable, $S_5(52-8) = S_1(26)$ | |
| | | | |
| 3 | 2 | minimal, $S_2(52-12) = S_1(26)$ | What is the risk of having the slope decision-making step when all are minimal?|
| | 3 | minimal, $S_3(52-12) = S_1(26)$ | |
| | 4 | minimal, $S_4(52-12) = S_1(26)$ | |
| | 5 | minimal, $S_5(52-12) = S_1(26)$ | |


```{r}
# Defining the log hazard function
log_haz_1 <- function(t, x, betas){
  lhaz <- log(betas[["shape"]]*(t ^(betas[["shape"]] - 1))) + 
    betas[["Intercept"]] +  
    betas[["regimen2"]]*x[["regimen2"]] +
    betas[["regimen3"]]*x[["regimen3"]] +
    betas[["regimen4"]]*x[["regimen4"]] +
    betas[["regimen5"]]*x[["regimen5"]] +
    betas[["duration.fun"]]*x[["duration.fun"]] # fixed duration effect
  
  return(lhaz)
}

true.coefs <- list(
  s97.even = c(
    shape = 0.425, # fixed p such that F(13) = 0.75*F(26)
    Intercept = log(uniroot(weibull_function,
                            interval = c(0,10),
                            p = 0.425,
                            surv.prop = 0.97, # S(26) = 97%
                            t = 26)$root),
    regimen2 = log(1.05),
    regimen3 = log(1.1),
    regimen4 = log(1.15),
    regimen5 = log(1.2),
    duration.fun = log(1.01)),
  s95.even = c(
    shape = 0.425, # fixed p such that F(13) = 0.75*F(26)
    Intercept = log(uniroot(weibull_function,
                            interval = c(0,10),
                            p = 0.425,
                            surv.prop = 0.95, # S(26) = 95%
                            t = 26)$root),
    regimen2 = log(1.05),
    regimen3 = log(1.1),
    regimen4 = log(1.15),
    regimen5 = log(1.2),
    duration.fun = log(1.01)),
  s90.even = c(
    shape = 0.425, # fixed p such that F(13) = 0.75*F(26)
    Intercept = log(uniroot(weibull_function,
                            interval = c(0,10),
                            p = 0.425,
                            surv.prop = 0.90, # S(26) = 90%
                            t = 26)$root),
    regimen2 = log(1.05),
    regimen3 = log(1.1),
    regimen4 = log(1.15),
    regimen5 = log(1.2),
    duration.fun = log(1.01))
)

xx <- df_temp %>% 
  # set up indicator functions
  mutate(regimen2 = ifelse(regimen == 2, 1, 0),
         regimen3 = ifelse(regimen == 3, 1, 0),
         regimen4 = ifelse(regimen == 4, 1, 0),
         regimen5 = ifelse(regimen == 5, 1, 0),
         # Set up duration function
         duration.fun = 26 - duration)

maxt <- 52-8
df_outcome <- map(true.coefs,
                  ~simsurv(dist = "weibull",
                           betas = .x,
                           loghazard = log_haz_1,
                           x = xx,
                           maxt = maxt) %>% 
                    bind_cols(df_temp))
```

```{r visualize-hazards}
df_vis <- xx %>% 
  dplyr::select(-patient.id, -enroll.day) %>% 
  unique()

tlist <- as.list(1:26)
names(tlist) <- 1:26
map_dfr(tlist, ~bind_cols(lhaz = log_haz_1(t = .x, 
                      x = df_vis, 
                      betas = true.coefs[[2]]), df_vis),
    .id = "t") %>% 
  mutate(regimen = as.factor(regimen),
         duration = as.factor(duration),
         t = as.numeric(t)) %>% 
  ggplot(aes(x = t, y = lhaz, col = duration)) +
  facet_wrap(~regimen) + 
  geom_line(aes(group = duration)) + 
  ylab("log[h(t)]") + 
  ggtitle("Log-hazard function over time", subtitle = "S(t) = 0.97, p = 0.4")
```


##### Setting up the hazard ratios

> (REMoxTB Figure 2)[https://www.nejm.org/doi/full/10.1056/NEJMoa1407426]. Panel A shows that the time until patients had an unfavorable outcome was shorter in the isoniazid group than in the control group (hazard ratio, 1.25 [97.5% CI, 1.08 to 1.42]) and was further reduced in the ethambutol group (hazard ratio, 1.21 [97.5% CI, 1.05 to 1.37]).

\[\begin{align}
S(t) &= e^{-\lambda t^p} \\
h(t) &= \lambda pt^{p-1}
\end{align}\]

## Generated data {.tabset .tabset-pills}

### Dataframe

```{r}
# Log10(TTP Dataset)
df_temp_long <- df_temp %>% 
  # Add in participant-level random effects
  left_join(Z) %>% 
  mutate(freq = 9) %>% # Weeks of TTP observation
  # Expand to weekly observation data
  uncount(freq)  %>%
  group_by(patient.id) %>% 
  mutate(patient.visit.day = (row_number() - 1)*7) %>% 
  rowwise() %>% 
  mutate(patient.visit.day = ifelse(patient.visit.day > 0, patient.visit.day + sample(-2:2,size = 1), patient.visit.day),
         # For use in regression
         patient.visit.week = patient.visit.day/7) %>% 
  # Generate residual error term for each time, eij, which is a draw from a normal distribution with mean 0 and SD equal to residual variability
  mutate(eij = rnorm(1, mean = 0, sd = sd_randomnoise)) %>%
  mutate(intercept = random.intercept + betas.log10ttp[1],
         control.slope = random.slope + betas.log10ttp[2]) %>% 
  rowwise() %>% 
  mutate(yij = intercept + control.slope*patient.visit.week + eij) %>%
  mutate(yij = ifelse(regimen > 1, yij + betas.log10ttp[regimen + 1]*patient.visit.week, yij)) %>% # relative % change for arm k
  mutate(log10ttp.censored = ifelse(yij > log10(lod), "right", "none"),
         yij_censored = ifelse(yij > log10(lod), log10(lod), yij)) %>%
  mutate(regimen = as.factor(regimen)) %>%
  dplyr::select(patient.id, enroll.day, regimen, duration, patient.visit.day, patient.visit.week, yij, log10ttp.censored, yij_censored) %>% 
  group_by(patient.id) %>% 
  mutate(interim1 = ifelse(max(patient.visit.day) + enroll.day < enroll.time.weeks*7, "included", "excluded"))
```

```{r}
df_temp_long %>%
  head(n = 30) %>%
  group_by(patient.id) %>%
  slice_head(n = 3) %>%
  arrange(enroll.day) %>%
  kable(caption = "First 3 observations for first 4 patients enrolled.",
        digits = 2) %>%
  kable_styling() 
```

### Data diagram {.tabset}

#### Randomization scheme 

```{r diagram-patient-data, fig.width=10,fig.height=8}
df_temp_long %>% 
  mutate(patient.id = factor(patient.id, levels = paste0("id", 1:(nkd*k*length(d))))) %>% 
  filter(enroll.day <= 5*7) %>% 
  ggplot(aes(x = enroll.time.weeks, y = patient.id, col = regimen, shape = as.factor(duration))) +
  geom_point(aes(x = (patient.visit.day + enroll.day)/7)) + 
  theme_bw() + 
  geom_vline(xintercept = c(0,16), 
             lty = 2,
             col = "darkgray") + 
  annotate("text", 
           x = 16, y = "id1", 
           label = "Interim 1",
           alpha = 0.7,
           hjust = -0.1,
           vjust = 0) +
  scale_x_continuous("Trial time (weeks)") #+ 
  # coord_cartesian(xlim = c(0,enroll.time.weeks+2))
```

#### Visualization of Follow-up

```{r}
df_outcome <- map(df_outcome,  
  ~mutate(.x, event.day = eventtime*7 + (enroll.day + 7*duration)) %>% 
  mutate(event.week.trial = event.day/7) %>% 
  mutate(observed = ifelse(event.day <= enroll.day + 365, "observed", "not observed")))

# df_outcome[[2]] %>% 
#   filter(patient.id %in% paste0("id",1:100)) %>% 
#   mutate(patient.id = factor(patient.id, levels = paste0("id", 1:nrow(df_outcome[[2]])))) %>% 
#   ggplot(aes(x = event.week.trial, y = patient.id, enroll.day)) +
#   geom_segment(aes(x = enroll.day/7, xend = enroll.day/7 + duration, yend = patient.id, col = as.factor(duration))) +
#   geom_segment(aes(x = enroll.day/7 + duration, xend = enroll.day/7 + 52, yend = patient.id),
#                col = "darkgray",
#                lty = 2) +
#   geom_point(data = filter(df_outcome[[2]], patient.id %in% paste0("id",1:100) & status == 1),
#              aes(x = event.week.trial),
#              alpha = 0.6) +
#   theme_bw() + 
#   labs(x = "Trial time (weeks)",
#        y = "Patient enrollment") + 
#   theme(axis.text.y = element_blank(),
#         axis.ticks.y = element_blank())

df_outcome[[2]] %>% 
  filter(patient.id %in% paste0("id",1:100)) %>% 
  mutate(patient.id = factor(patient.id, levels = paste0("id", 1:nrow(df_outcome[[2]]))),
         regimen = factor(regimen, levels = 1:5)) %>% 
  ggplot(aes(x = event.week.trial, y = patient.id)) +
  geom_segment(aes(x = enroll.day/7, xend = enroll.day/7 + duration, yend = patient.id, col = regimen)) +
  geom_segment(aes(x = enroll.day/7 + duration, xend = enroll.day/7 + 52, yend = patient.id),
               col = "darkgray",
               lty = 2) +
  geom_point(data = filter(df_outcome[[2]], patient.id %in% paste0("id",1:100) & status == 1),
             aes(x = event.week.trial),
             alpha = 0.6) +
  theme_bw() + 
  labs(x = "Trial time (weeks)",
       y = "Patient enrollment") + 
  ggtitle("Weibull parameterization (p = 0.4)") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

#### Visualizing when (observed) failure events occur

```{r}
df_outcome[[1]] %>% 
  filter(status == 1 & observed == "observed") %>%
  ggplot(aes(x = event.week.trial, y = patient.id)) +
  geom_segment(aes(x = enroll.day/7, xend = enroll.day/7 + duration, yend = patient.id, col = as.factor(duration))) +
  geom_segment(aes(x = enroll.day/7 + duration, xend = enroll.day/7 + 52, yend = patient.id), 
               col = "darkgray",
               lty = 2) + 
  geom_point(aes(x = event.week.trial),
             alpha = 0.6) + 
  theme_bw() +
  scale_x_continuous("Trial time (weeks)") +
  ggtitle("Exponential parameterization")

df_outcome[[2]] %>% 
  filter(status == 1 & observed == "observed") %>%
  ggplot(aes(x = event.week.trial, y = patient.id)) +
  geom_segment(aes(x = enroll.day/7, xend = enroll.day/7 + duration, yend = patient.id, col = as.factor(duration))) +
  geom_segment(aes(x = enroll.day/7 + duration, xend = enroll.day/7 + 52, yend = patient.id), 
               col = "darkgray",
               lty = 2) + 
  geom_point(aes(x = event.week.trial),
             alpha = 0.6) + 
  theme_bw() +
  scale_x_continuous("Trial time (weeks)")+
  ggtitle("Weibull parameterization (p = 0.4)")
```
