---
title: "Random Intercept, Random Slope"
author: "Suzanne Dufault"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../graphs/simulation-results/random-intercept-random-slope/")

library(tidyverse)
library(patchwork)
library(jpeg) # https://www.geeksforgeeks.org/how-to-add-image-to-ggplot2-in-r/
library(here)
library(kableExtra)
library(latex2exp)
library(furrr)
library(patchwork)
source(here("lib", "ucsf-color-palette.R"))
options(knitr.kable.NA = '')
source(here("lib", "target-product-profile-function.R"))
source(here("lib", "mcmc-rank-function.R"))
source(here("lib", "mcmc-compare-v-control.R"))
```

# Output {.tabset}

## Settings

```{r lineplot-simulating-ttp}
# Call in model being used as "truth"
load("~/Library/CloudStorage/OneDrive-UCSF/ucsf-research/phase2b-simstudy/data/bayes-generated/2021-12-14_remox-lmm-short.RData")

# Pull out coefficients
s <- summary(fit.cens)
betas_orig <- c(s$fixed$Estimate)

p0 <- data.frame(Control = betas_orig[1] + betas_orig[2]*0:8,
           Regimen1 = betas_orig[1] + betas_orig[2]*0:8 + betas_orig[3]*0:8,
           Regimen2 = betas_orig[1] + betas_orig[2]*0:8 + betas_orig[4]*0:8,
           weeks = 0:8) %>% 
  pivot_longer(cols = 1:3,
               values_to = "log10(TTP)",
               names_to = "Regimen") %>% 
  ggplot(aes(x = weeks, y = 10^(`log10(TTP)`), col = Regimen)) + 
  geom_line() + 
  scale_y_log10("TTP in days, log10 scale",
                breaks = c(5,7,10,15,20,25,35),
                labels = c(5,7,10,15,20,25,35)) + 
  scale_x_continuous("Days from randomization",
                     breaks = 0:8,
                     labels = seq(0,56, by = 7)) + 
  scale_color_manual(values = ucsf_col_pal,
                     labels = c(1:3)) +
  scale_linetype_discrete(labels = c(1:3)) +
  coord_cartesian(ylim = c(7,35)) + 
  ggtitle("Original REMoxTB data",
          subtitle = "Linear Bayesian hierarchical model") + 
  theme_bw()

betas_orig <- c(s$fixed$Estimate)[1:2] # (just the intercept and control group slope for now)

slopes_even <- seq(0.1,0.4,by = 0.1)
beta_Regimens <- betas_orig[2]*slopes_even # multiplying the control group slope by the a priori %change
betas <- c(betas_orig, beta_Regimens) # length k+1 (intercept + slopes per K Regimens)

p1 <- data.frame(Control = betas[1] + betas[2]*0:8,
           Regimen1 = betas[1] + betas[2]*0:8 + betas[3]*0:8,
           Regimen2 = betas[1] + betas[2]*0:8 + betas[4]*0:8,
           Regimen3 = betas[1] + betas[2]*0:8 + betas[5]*0:8,
           Regimen4 = betas[1] + betas[2]*0:8 + betas[6]*0:8,
           weeks = 0:8) %>% 
  pivot_longer(cols = 1:5,
               values_to = "log10(TTP)",
               names_to = "Regimen") %>% 
  ggplot(aes(x = weeks, y = 10^(`log10(TTP)`), col = Regimen, lty = Regimen)) + 
  geom_line() + 
  scale_y_log10("TTP in days, log10 scale",
                breaks = c(5,7,10,15,20,25,35),
                labels = c(5,7,10,15,20,25,35)) + 
  scale_x_continuous("Days from randomization",
                     breaks = 0:8,
                     labels = seq(0,56, by = 7)) + 
  scale_color_manual(values = ucsf_col_pal,
                     labels = c(1:5)) +
  scale_linetype_discrete(labels = c(1:5)) +
  coord_cartesian(ylim = c(7,35)) + 
  ggtitle("Even condition", subtitle = c("10%, 20%, 30%, 40%")) + 
  theme_bw()

slopes_highlow <- c(-.1, .1, .35, .4)
beta_Regimens <- betas_orig[2]*slopes_highlow # multiplying the control group slope by the a priori %change
betas <- c(betas_orig, beta_Regimens) # length k+1 (intercept + slopes per K Regimens)

p2 <- data.frame(Control = betas[1] + betas[2]*0:8,
           Regimen1 = betas[1] + betas[2]*0:8 + betas[3]*0:8,
           Regimen2 = betas[1] + betas[2]*0:8 + betas[4]*0:8,
           Regimen3 = betas[1] + betas[2]*0:8 + betas[5]*0:8,
           Regimen4 = betas[1] + betas[2]*0:8 + betas[6]*0:8,
           weeks = 0:8) %>% 
  pivot_longer(cols = 1:5,
               values_to = "log10(TTP)",
               names_to = "Regimen") %>% 
  ggplot(aes(x = weeks, y = 10^(`log10(TTP)`), col = Regimen, lty = Regimen)) + 
  geom_line() + 
  scale_y_log10("TTP in days, log10 scale",
                breaks = c(5,7,10,15,20,25,35),
                labels = c(5,7,10,15,20,25,35)) + 
  scale_x_continuous("Days from randomization",
                     breaks = 0:8,
                     labels = seq(0,56, by = 7)) +
  scale_color_manual(values = ucsf_col_pal,
                     labels = c(1:5)) +
  scale_linetype_discrete(labels = c(1:5)) +
  coord_cartesian(ylim = c(7,35)) + 
  ggtitle("High-low condition", subtitle = c("-10%, 10%, 35%, 40%")) + 
  theme_bw()

slopes_high <- c(.35, .37, .39, .41)
beta_Regimens <- betas_orig[2]*slopes_high # multiplying the control group slope by the a priori %change
betas <- c(betas_orig, beta_Regimens) # length k+1 (intercept + slopes per K Regimens)

p3 <- data.frame(Control = betas[1] + betas[2]*0:8,
           Regimen1 = betas[1] + betas[2]*0:8 + betas[3]*0:8,
           Regimen2 = betas[1] + betas[2]*0:8 + betas[4]*0:8,
           Regimen3 = betas[1] + betas[2]*0:8 + betas[5]*0:8,
           Regimen4 = betas[1] + betas[2]*0:8 + betas[6]*0:8,
           weeks = 0:8) %>% 
  pivot_longer(cols = 1:5,
               values_to = "log10(TTP)",
               names_to = "Regimen") %>% 
  ggplot(aes(x = weeks, y = 10^(`log10(TTP)`), col = Regimen, lty = Regimen)) + 
  geom_line() + 
  scale_y_log10("TTP in days, log10 scale",
                breaks = c(5,7,10,15,20,25,35),
                labels = c(5,7,10,15,20,25,35)) + 
  scale_x_continuous("Days from randomization",
                     breaks = 0:8,
                     labels = seq(0,56, by = 7)) + 
  scale_color_manual(values = ucsf_col_pal,
                     labels = c(1:5)) +
  scale_linetype_discrete(labels = c(1:5)) +
  coord_cartesian(ylim = c(7,35)) + 
  ggtitle("High condition", subtitle = c("35%, 37%, 39%, 41%")) + 
  theme_bw()

ttp_fig <- gridExtra::grid.arrange(p0,p1,p2,p3)
```

```{r fig.width=10, fig.height=5}
library(magick)
survival_fig <- image_ggplot(image_read(here("graphs", "simulation-settings","2022-03-22_survival-curve-general.jpg")))
ggpubr::ggarrange(ttp_fig, survival_fig,
                  widths = c(3,2),
                  labels = "AUTO",
                  heights = 1)
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-settings",
                       paste0(Sys.Date(), "_ttp-relapse-simulation-settings.jpeg")),
       device = "jpeg",
       units = "in",
       width = 10,
       height = 5)
```

## Unfavorable Outcome 

```{r relapse-data}
# Situation 1, S(52) = .95
load(here("data","analyzed","2022-03-07_s95-situation1-results_nk30_4mo-duration.RData"))
s95.sit1.30 <- s95.situation1.results
load(here("data","analyzed","2022-03-07_s95-situation1-results_nk40_4mo-duration.RData"))
s95.sit1.40 <- s95.situation1.results
load(here("data","analyzed","2022-03-07_s95-situation1-results_nk60_4mo-duration.RData"))
s95.sit1.60 <- s95.situation1.results
load(here("data","analyzed","2022-03-07_s95-situation1-results_nk80_4mo-duration.RData"))
s95.sit1.80 <- s95.situation1.results; rm(s95.situation1.results)
```

```{r fig-relapse-data, fig.width = 7, fig.height = 9}
bind_rows(mutate(s95.sit1.30, nk = 30),
          mutate(s95.sit1.40, nk = 40),
          mutate(s95.sit1.60, nk = 60),
          mutate(s95.sit1.80, nk = 80)) %>% 
  group_by(nk, regimen) %>% 
  summarise(prop_stopped_1 = mean(n_relapse_interim1 >= 1),
            prop_stopped_2 = mean(n_relapse_interim1 >= 2),
            prop_stopped_3 = mean(n_relapse_interim1 >= 3)) %>% 
  ungroup() %>% 
  pivot_longer(cols = prop_stopped_1:prop_stopped_3,
               names_to = "threshold",
               values_to = "prop_stopped") %>% 
  filter(!regimen %in%  c(1,3)) %>% #removing control and one of the minimal regimens
  mutate(rate = case_when(regimen == 2 ~ "Sub-optimal: 10% Unfavorable Outcome Rate",
                          regimen == 4 ~ "Minimal: 5% Unfavorable Outcome Rate",
                          regimen == 5 ~ "Desirable: 2.5% Unfavorable Outcome Rate"),
         threshold = str_remove(threshold, "prop_stopped_")) %>% 
  mutate(rate = factor(rate, levels = c("Sub-optimal: 10% Unfavorable Outcome Rate","Minimal: 5% Unfavorable Outcome Rate","Desirable: 2.5% Unfavorable Outcome Rate"))) %>% 
  ggplot(aes(x = prop_stopped,
             y = nk, 
             # shape = threshold, 
             col = threshold)) + 
  facet_wrap(~rate, ncol = 1) + 
  scale_x_continuous(TeX("Pr(No. relapses $\\geq$ threshold)"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_y_continuous(TeX("$n_k$"), breaks = c(30,40,60,80), labels = c(30,40,60,80)) +
  scale_linetype_discrete("Unfavorable outcome threshold") +
  scale_color_manual("Unfavorable outcome threshold", values = ucsf_col_pal) + 
  geom_line(aes(lty = threshold),
            size = 1) +
  ggpubr::theme_pubr()

bind_rows(mutate(s95.sit1.30, nk = 30),
          mutate(s95.sit1.40, nk = 40),
          mutate(s95.sit1.60, nk = 60),
          mutate(s95.sit1.80, nk = 80)) %>% 
  group_by(nk, regimen) %>% 
  summarise(prop_stopped_1 = mean(n_relapse_interim1 >= 1),
            prop_stopped_2 = mean(n_relapse_interim1 >= 2),
            prop_stopped_3 = mean(n_relapse_interim1 >= 3)) %>% 
  ungroup() %>% 
  pivot_longer(cols = prop_stopped_1:prop_stopped_3,
               names_to = "threshold",
               values_to = "prop_stopped") %>% 
  filter(!regimen %in%  c(1,3)) %>% #removing control and one of the minimal regimens
  mutate(rate = case_when(regimen == 2 ~ "Sub-optimal: 10% Unfavorable Outcome Rate",
                          regimen == 4 ~ "Minimal: 5% Unfavorable Outcome Rate",
                          regimen == 5 ~ "Desirable: 2.5% Unfavorable Outcome Rate"),
         threshold = str_remove(threshold, "prop_stopped_")) %>% 
  mutate(rate = factor(rate, levels = c("Sub-optimal: 10% Unfavorable Outcome Rate","Minimal: 5% Unfavorable Outcome Rate","Desirable: 2.5% Unfavorable Outcome Rate"))) %>% 
  ggplot(aes(x = prop_stopped,
             y = nk, 
             # shape = threshold, 
             col = threshold)) + 
  facet_wrap(~rate, ncol = 1) + 
  scale_x_continuous(TeX("Pr(No. relapses $\\geq$ threshold)"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_y_continuous(TeX("$n_k$"), breaks = c(30,40,60,80), labels = c(30,40,60,80)) +
  scale_linetype_discrete("Unfavorable outcome threshold") +
  scale_color_manual("Unfavorable outcome threshold", values = ucsf_col_pal) + 
  geom_point() + 
  # geom_line(aes(lty = threshold),
  #           size = 1) +
  ggpubr::theme_pubr()

bind_rows(mutate(s95.sit1.30, nk = 30),
          mutate(s95.sit1.40, nk = 40),
          mutate(s95.sit1.60, nk = 60),
          mutate(s95.sit1.80, nk = 80)) %>% 
  group_by(nk, regimen) %>% 
  summarise(prop_stopped_1 = mean(n_relapse_interim1 >= 1),
            prop_stopped_2 = mean(n_relapse_interim1 >= 2),
            prop_stopped_3 = mean(n_relapse_interim1 >= 3)) %>% 
  ungroup() %>% 
  pivot_longer(cols = prop_stopped_1:prop_stopped_3,
               names_to = "threshold",
               values_to = "prop_stopped") %>% 
  filter(!regimen %in%  c(1,3)) %>% #removing control and one of the minimal regimens
  mutate(rate = case_when(regimen == 2 ~ "Sub-optimal: 10% Unfavorable Outcome Rate",
                          regimen == 4 ~ "Minimal: 5% Unfavorable Outcome Rate",
                          regimen == 5 ~ "Desirable: 2.5% Unfavorable Outcome Rate"),
         threshold = str_remove(threshold, "prop_stopped_")) %>% 
  mutate(rate = factor(rate, levels = c("Sub-optimal: 10% Unfavorable Outcome Rate","Minimal: 5% Unfavorable Outcome Rate","Desirable: 2.5% Unfavorable Outcome Rate"))) %>% 
  ggplot(aes(x = as.factor(nk),
             y = threshold, 
             # shape = threshold, 
             fill = prop_stopped)) + 
  facet_wrap(~rate, ncol = 1) + 
  geom_tile() + 
  geom_text(aes(label = format(round(prop_stopped, 2), nsmall = 2)),
            col = "white") +
  ggpubr::theme_pubr() + 
  scale_y_discrete("Unfavorable outcome threshold") +
  scale_x_discrete(TeX("$n_k$"), breaks = c(30,40,60,80), labels = c(30,40,60,80)) + 
  scale_fill_viridis_c(TeX("Pr(No. observed unfavorable outcomes $\\geq$ threshold)")) + 
  theme(legend.position = "bottom")

```

```{r eval= FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                       paste0(Sys.Date(), "_relapse-thresholds.jpg")),
       device = "jpg",
       height = 6,
       width = 5.5,
       units = "in")

ggsave(filename = here("graphs", "submission", "fig-03_relapse-thresholds.eps"),
       device = "eps",
       height = 6,
       width = 5.75,
       units = "in")
```

```{r eval = FALSE}
bind_rows(mutate(s95.sit1.30, nk = 30),
          mutate(s95.sit1.40, nk = 40),
          mutate(s95.sit1.60, nk = 60),
          mutate(s95.sit1.80, nk = 80)) %>% 
  group_by(nk, regimen) %>% 
  summarise(prop_stopped_1 = mean(n_relapse_interim1 >= 1),
            prop_stopped_2 = mean(n_relapse_interim1 >= 2),
            prop_stopped_3 = mean(n_relapse_interim1 >= 3)) %>% 
  ungroup() %>% 
  pivot_longer(cols = prop_stopped_1:prop_stopped_3,
               names_to = "threshold",
               values_to = "prop_stopped") %>% 
  filter(!regimen %in%  c(1,3)) %>% #removing control and one of the minimal regimens
  mutate(rate = case_when(regimen == 2 ~ "Sub-optimal: 10% Unfavorable Outcome Rate",
                          regimen == 4 ~ "Minimal: 5% Unfavorable Outcome Rate",
                          regimen == 5 ~ "Desirable: 2.5% Unfavorable Outcome Rate"),
         threshold = str_remove(threshold, "prop_stopped_")) %>% 
  mutate(rate = factor(rate, levels = c("Sub-optimal: 10% Unfavorable Outcome Rate","Minimal: 5% Unfavorable Outcome Rate","Desirable: 2.5% Unfavorable Outcome Rate"))) %>% 
  ggplot(aes(x = as.factor(nk),
             y = threshold, 
             # shape = threshold, 
             fill = prop_stopped)) + 
  ggtitle("Dufault Fig 3. (Top)") +
  facet_wrap(~rate, ncol = 1) + 
  geom_tile() + 
  geom_text(aes(label = format(round(prop_stopped, 2), nsmall = 2)),
            col = "white") +
  ggpubr::theme_pubr() + 
  scale_y_discrete("Unfavorable outcome threshold") +
  scale_x_discrete(TeX("$n_k$"), breaks = c(30,40,60,80), labels = c(30,40,60,80)) + 
  scale_fill_viridis_c(TeX("Pr(No. observed unfavorable outcomes $\\geq$ threshold)")) + 
  theme(legend.position = "bottom")

ggsave(filename = here("graphs", "submission", "fig-03_relapse-thresholds_annotated.eps"),
       device = "eps",
       dpi = 600,
       height = 6,
       width = 5.75,
       units = "in")
```

```{r}
bind_rows(mutate(s95.sit1.30, nk = 30),
          mutate(s95.sit1.40, nk = 40),
          mutate(s95.sit1.60, nk = 60),
          mutate(s95.sit1.80, nk = 80)) %>% 
  group_by(nk, regimen) %>% 
  summarise(prop_stopped_1 = mean(n_relapse_interim1 >= 1),
            prop_stopped_2 = mean(n_relapse_interim1 >= 2),
            prop_stopped_3 = mean(n_relapse_interim1 >= 3),
            prop_stopped_4 = mean(n_relapse_interim1 >= 4),
            prop_stopped_5 = mean(n_relapse_interim1 >= 5)) %>% 
  ungroup() %>% 
  pivot_longer(cols = prop_stopped_1:prop_stopped_5,
               names_to = "threshold",
               values_to = "prop_stopped") %>% 
  filter(!regimen %in%  c(1,3)) %>% #removing control and one of the minimal regimens
  mutate(rate = case_when(regimen == 2 ~ "Sub-optimal: 10% Unfavorable Outcome Rate",
                          regimen == 4 ~ "Minimal: 5% Unfavorable Outcome Rate",
                          regimen == 5 ~ "Desirable: 2.5% Unfavorable Outcome Rate"),
         threshold = str_remove(threshold, "prop_stopped_")) %>% 
  mutate(rate = factor(rate, levels = c("Sub-optimal: 10% Unfavorable Outcome Rate","Minimal: 5% Unfavorable Outcome Rate","Desirable: 2.5% Unfavorable Outcome Rate"))) %>% 
  ggplot(aes(x = as.factor(nk),
             y = threshold, 
             # shape = threshold, 
             fill = prop_stopped)) + 
  facet_wrap(~rate, ncol = 1) + 
  geom_tile() + 
  geom_text(aes(label = format(round(prop_stopped, 2), nsmall = 2)),
            col = "white") +
  ggpubr::theme_pubr() + 
  scale_y_discrete("Unfavorable Outcome threshold") +
  scale_x_discrete(TeX("$n_k$"), breaks = c(30,40,60,80), labels = c(30,40,60,80)) + 
  scale_fill_viridis_c(TeX("Pr(No. observed relapses $\\geq$ threshold)")) + 
  theme(legend.position = "bottom")
```

## TTP {.tabset .tabset-pills}

### Target Product Profile Decisions

```{r tpp-decision-function}
# generated by analysis/03_tpp-decisions.R
load(here("data", "analyzed", "target-product-profile", "2022-07-07_tpp-decisions.RData"))
```

```{r}
d_hl <- decisions$decisions_highlow %>% 
  filter(Regimen == "Regimen 1") %>% 
  mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "-10%"))
d_full <- decisions$decisions_even %>% 
  mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "10%",
                             Regimen == "Regimen 2" ~ "20%",
                             Regimen == "Regimen 3" ~ "30%",
                             Regimen == "Regimen 4" ~ "40%")) %>% 
  bind_rows(d_hl) %>%
  mutate(Decision = factor(Decision, levels = c("NO-GO", "Continue", "GO")),
         nk = factor(nk)) %>% 
  group_by(Regimen, nk, Decision) %>% 
  summarise(n = n_distinct(sim)) %>% 
  group_by(Regimen, nk) %>% 
  summarise(Probability = n/sum(n),
            Decision = Decision) 

d_full %>% 
  ungroup() %>% 
  pivot_wider(values_from = Probability,
              names_from = Decision) %>% 
  dplyr::select(-Regimen) %>% 
  kable(digits = 2,
        caption = "Decision percentages when tau_LRV = tau_TV = 0.025") %>% 
  kable_styling() %>% 
  group_rows("Slope, %: -10%", start_row = 1, end_row = 5) %>% 
  group_rows("Slope, %: 10%", start_row = 6, end_row = 10) %>%
  group_rows("Slope, %: 20%", start_row = 11, end_row = 15) %>% 
  group_rows("Slope, %: 30%", start_row = 16, end_row = 20) %>% 
  group_rows("Slope, %: 40%", start_row = 21, end_row = 25)
```

```{r barplot-tpp-decisions, fig.width = 10, fig.height = 6, fig.cap = "When theta_lrv = 0, theta_TV = 20, tau_LRV = tau_TV = 0.025."}
d_full %>% 
  ggplot(aes(x = nk, y = Probability, fill = Decision)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~Regimen, nrow = 1) +
  scale_y_continuous("Decision Probability",
                     breaks = seq(0,1,by = 0.1),
                     labels = seq(0,1,by = 0.1)) +
  scale_fill_manual(values = c("red", ucsf_col_pal[8], ucsf_col_pal[4]),
                    breaks = c("NO-GO", "Continue", "GO"),
                    labels = c("NO-GO", "Continue", "GO")) +
  xlab(TeX("$n_k$")) + 
  # ggtitle("", subtitle = TeX("$\\theta_{LRV} = 0%, \\theta_{TV} = 20%, \\tau_{LRV} = \\tau_{TV} = 0.025$")) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "bottom")
```

```{r eval=false}
ggsave(filename = here("graphs", "submission", "fig-04_barplot-tpp-decisions.eps"),
       device = "eps",
       height = 6,
       width = 9,
       units = "in")
```

```{r eval = FALSE}
d_full %>% 
  ggplot(aes(x = nk, y = Probability, fill = Decision)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~Regimen, nrow = 1) +
  scale_y_continuous("Decision Probability",
                     breaks = seq(0,1,by = 0.1),
                     labels = seq(0,1,by = 0.1)) +
  scale_fill_manual(values = c("red", ucsf_col_pal[8], ucsf_col_pal[4]),
                    breaks = c("NO-GO", "Continue", "GO"),
                    labels = c("NO-GO", "Continue", "GO")) +
  xlab(TeX("$n_k$")) + 
  ggtitle("Dufault Fig. 4 (Top)") +
  # ggtitle("", subtitle = TeX("$\\theta_{LRV} = 0%, \\theta_{TV} = 20%, \\tau_{LRV} = \\tau_{TV} = 0.025$")) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "bottom")

ggsave(filename = here("graphs", "submission", "fig-04_barplot-tpp-decisions_annotated.eps"),
       device = "eps",
       dpi = 600,
       height = 6,
       width = 9,
       units = "in")
```

```{r areaplot-tpp-decisions, fig.width = 10, fig.height = 6, fig.cap = "When theta_lrv = 0, theta_TV = 20, tau_LRV = tau_TV = 0.025.", eval = FALSE}
d_full %>% 
  mutate(nk_num = case_when(nk == "20" ~ 20,
                            nk == "30" ~ 30,
                            nk == "40" ~ 40,
                            nk == "60" ~ 60,
                            nk == "80" ~ 80)) %>% 
  ggplot(aes(x = nk_num, y = Probability, fill = Decision)) + 
  # geom_bar(stat = "identity") + 
  geom_area() + 
  facet_wrap(~Regimen, nrow = 1) +
  scale_y_continuous("Decision Probability",
                     breaks = seq(0,1,by = 0.1),
                     labels = seq(0,1,by = 0.1)) +
  scale_fill_manual(values = c("red", ucsf_col_pal[8], ucsf_col_pal[4]),
                    breaks = c("NO-GO", "Continue", "GO"),
                    labels = c("NO-GO", "Continue", "GO")) +
  xlab(TeX("$n_k$")) + 
  # ggtitle("", subtitle = TeX("$\\theta_{LRV} = 0%, \\theta_{TV} = 20%, \\tau_{LRV} = \\tau_{TV} = 0.025$")) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "bottom")
```

<!-- # ```{r decisions-2, cache = TRUE} -->
<!-- # plan(multisession) -->
<!-- # nk <- as.list(c(20,30,40,60,80)) -->
<!-- # names(nk) <- nk -->
<!-- # decisions_2 <- future_map2_dfr(mcmc_even, nk, ~decision_function(.x, -->
<!-- #                                                                nk = .y, -->
<!-- #                                                                theta_lrv = 0, # in % -->
<!-- #                                                                theta_tv = 20, # in %  -->
<!-- #                                                                tau_lrv = 0.05,  -->
<!-- #                                                                tau_tv = 0.05)) -->
<!-- #  -->
<!-- # decisions_highlow_2 <- future_map2_dfr(mcmc_highlow, nk, ~decision_function(.x, -->
<!-- #                                                                           nk = .y, -->
<!-- #                                                                           theta_lrv = 0, # in % -->
<!-- #                                                                           theta_tv = 20, # in %  -->
<!-- #                                                                           tau_lrv = 0.05,  -->
<!-- #                                                                           tau_tv = 0.05)) -->
<!-- # ``` -->

<!-- ```{r} -->
<!-- d_hl_2 <- decisions_highlow_2 %>% -->
<!--   filter(Regimen == "Regimen 1") %>% -->
<!--   mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "-10%")) -->
<!-- d_full_2 <- decisions_2 %>% -->
<!--   mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "10%", -->
<!--                              Regimen == "Regimen 2" ~ "20%", -->
<!--                              Regimen == "Regimen 3" ~ "30%", -->
<!--                              Regimen == "Regimen 4" ~ "40%")) %>% -->
<!--   bind_rows(d_hl) %>% -->
<!--   mutate(Decision = factor(Decision, levels = c("NO-GO", "Continue", "GO")), -->
<!--          nk = factor(nk)) %>% -->
<!--   group_by(Regimen, nk, Decision) %>% -->
<!--   summarise(n = n_distinct(sim)) %>% -->
<!--   group_by(Regimen, nk) %>% -->
<!--   summarise(Probability = n/sum(n), -->
<!--             Decision = Decision) -->

<!-- d_full_2 %>% -->
<!--   ungroup() %>% -->
<!--   pivot_wider(values_from = Probability, -->
<!--               names_from = Decision) %>% -->
<!--   dplyr::select(-Regimen) %>% -->
<!--   kable(digits = 2, -->
<!--         caption = "Decision percentages when tau_LRV = tau_TV = 0.05") %>% -->
<!--   kable_styling() %>% -->
<!--   group_rows("Slope, %: -10%", start_row = 1, end_row = 5) %>% -->
<!--   group_rows("Slope, %: 10%", start_row = 6, end_row = 10) %>% -->
<!--   group_rows("Slope, %: 20%", start_row = 11, end_row = 15) %>% -->
<!--   group_rows("Slope, %: 30%", start_row = 16, end_row = 20) %>% -->
<!--   group_rows("Slope, %: 40%", start_row = 21, end_row = 25) -->
<!-- ``` -->

```{r}
load(here("data","cleaned","2022-06-22_mcmc_random-intercept-random-slope_nk-30_even.RData"))
```

```{r area-plot_different-tv-lrv-risk, cache = TRUE}
# Even

tau_tv <- list(0.025, 0.025, 0.025, 0.025, 0.025)
names(tau_tv) <- tau_tv
tau_lrv <- list(0.025, 0.05, 0.1, 0.15, 0.2)
names(tau_lrv) <- tau_lrv

d30 <- NULL
for (i in 1:length(tau_lrv)){
  out <- map_dfr(list(mcmc_mods_even_30),
                 ~decision_function(mcmc_list = .x,
                                    nk = 30,
                                    theta_lrv = 0,
                                    theta_tv = 20,
                                    tau_lrv = tau_lrv[[i]],
                                    tau_tv = tau_tv[[i]]))
  out <- out %>% mutate(tau_lrv = tau_lrv[[i]])
  d30 <- bind_rows(d30, out)
}


d30 %>% 
  group_by(tau_lrv, Regimen, Decision) %>% 
  summarise(n = n()) %>% 
  group_by(tau_lrv, Regimen) %>% 
  summarise(prop = n/sum(n),
            Decision = factor(Decision, levels = c("NO-GO", "Continue", "GO"))) %>% 
  mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "10%",
                             Regimen == "Regimen 2" ~ "20%",
                             Regimen == "Regimen 3" ~ "30%",
                             Regimen == "Regimen 4" ~ "40%")) %>% 
  ggplot(aes(x = tau_lrv, y = prop, fill = Decision)) + 
  facet_wrap(~Regimen) +
  # geom_bar(stat="identity") + 
  geom_area() +
  scale_fill_manual(values = c("red", ucsf_col_pal[8], ucsf_col_pal[4]),
                    breaks = c("NO-GO", "Continue", "GO"),
                    labels = c("NO-GO", "Continue", "GO")) +
  ggpubr::theme_pubr() + 
  xlab(TeX("$\\tau_{LRV}")) +
  scale_y_continuous("Decision Probability",
                     breaks = seq(0,1,by = 0.1),
                     labels = seq(0,1,by = 0.1)) +
  theme(legend.position = "bottom")


tau_lrv <- list(0.025, 0.025, 0.025, 0.025, 0.025)
names(tau_lrv) <- tau_lrv
tau_tv <- list(0.025, 0.05, 0.1, 0.15, 0.2)
names(tau_tv) <- tau_tv

d30_tv <- NULL
for (i in 1:length(tau_lrv)){
  out <- map_dfr(list(mcmc_mods_even_30),
                 ~decision_function(mcmc_list = .x,
                                    nk = 30,
                                    theta_lrv = 0,
                                    theta_tv = 20,
                                    tau_lrv = tau_lrv[[i]],
                                    tau_tv = tau_tv[[i]]))
  out <- out %>% mutate(tau_tv = tau_tv[[i]])
  d30_tv <- bind_rows(d30_tv, out)
}

d30_tv %>% 
  group_by(tau_tv, Regimen, Decision) %>% 
  summarise(n = n()) %>% 
  group_by(tau_tv, Regimen) %>% 
  summarise(prop = n/sum(n),
            Decision = factor(Decision, levels = c("NO-GO", "Continue", "GO"))) %>% 
  mutate(Regimen = case_when(Regimen == "Regimen 1" ~ "-10%",
                             Regimen == "Regimen 2" ~ "10%",
                             Regimen == "Regimen 3" ~ "35%",
                             Regimen == "Regimen 4" ~ "40%")) %>% 
  ggplot(aes(x = tau_tv, y = prop, fill = Decision)) + 
  facet_wrap(~Regimen) +
  # geom_bar(stat="identity") + 
  geom_area() +
  scale_fill_manual(values = c("red", ucsf_col_pal[8], ucsf_col_pal[4]),
                    breaks = c("NO-GO", "Continue", "GO"),
                    labels = c("NO-GO", "Continue", "GO")) +
  ggpubr::theme_pubr() + 
  xlab(TeX("$\\tau_{TV}")) +
  scale_y_continuous("Decision Probability",
                     breaks = seq(0,1,by = 0.1),
                     labels = seq(0,1,by = 0.1)) +
  theme(legend.position = "bottom")
```

### Ranking 

```{r }
load(here("data", "analyzed", "ranking", "2022-07-07_ranking-probabilities.RData"))
```

#### $\psi_1$: Comparing Against Control

```{r }
load(here("data", "analyzed", "ranking", "2022-07-07_compare-v-control.RData"))

p30 <- comparisons %>%
  filter(nk == "nk30") %>%
  mutate(condition = factor(condition, levels = c("Even", "High-low", "High"))) %>% 
  pivot_longer(cols = p.regimen.2.v.control:p.regimen.5.v.control,
               names_to = "comparison",
               values_to = "posterior") %>% 
  mutate(comparison = case_when(comparison == "p.regimen.5.v.control" ~ "$\\theta_{5}$",
                                comparison == "p.regimen.4.v.control" ~ "$\\theta_{4}$",
                                comparison == "p.regimen.3.v.control" ~ "$\\theta_{3}$",
                                comparison == "p.regimen.2.v.control" ~ "$\\theta_{2}$")) %>% 
  ggplot(aes(y = comparison, x = posterior)) + 
  facet_wrap(~condition, ncol = 1) + 
  geom_point(position = position_jitter(width = 0, height = 0.35),
             aes(col = comparison),
             alpha = 0.5) +
  geom_boxplot(alpha = 0.3, # NEED TO INCORPORATE SAMPLE SIZE!!!
               width = 0.3,
               outlier.shape = NA,
               col = "white") +
  scale_color_manual(values = ucsf_col_pal) +
  scale_y_discrete(labels = TeX) +
  scale_x_continuous(TeX("$Pr_{\\theta}(\\theta > \\theta_1 | X)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  ggpubr::theme_pubr() +
  theme(legend.position = "none",
        axis.title.y = element_blank())

p40 <- comparisons %>%
  filter(nk == "nk40") %>%
  mutate(condition = factor(condition, levels = c("Even", "High-low", "High"))) %>% 
  pivot_longer(cols = p.regimen.2.v.control:p.regimen.5.v.control,
               names_to = "comparison",
               values_to = "posterior") %>% 
  mutate(comparison = case_when(comparison == "p.regimen.5.v.control" ~ "$\\theta_{5}$",
                                comparison == "p.regimen.4.v.control" ~ "$\\theta_{4}$",
                                comparison == "p.regimen.3.v.control" ~ "$\\theta_{3}$",
                                comparison == "p.regimen.2.v.control" ~ "$\\theta_{2}$")) %>% 
  ggplot(aes(y = comparison, x = posterior)) + 
  facet_wrap(~condition, ncol = 1) + 
  geom_point(position = position_jitter(width = 0, height = 0.35),
             aes(col = comparison),
             alpha = 0.5) +
  geom_boxplot(alpha = 0.3, # NEED TO INCORPORATE SAMPLE SIZE!!!
               width = 0.3,
               outlier.shape = NA,
               col = "white") +
  scale_color_manual(values = ucsf_col_pal) +
  scale_y_discrete(labels = TeX) +
  scale_x_continuous(TeX("$Pr_{\\theta}(\\theta > \\theta_1 | X)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  ggpubr::theme_pubr() +
  theme(legend.position = "none",
        axis.title.y = element_blank())

p60 <- comparisons %>%
  filter(nk == "nk60") %>%
  mutate(condition = factor(condition, levels = c("Even", "High-low", "High"))) %>% 
  pivot_longer(cols = p.regimen.2.v.control:p.regimen.5.v.control,
               names_to = "comparison",
               values_to = "posterior") %>% 
  mutate(comparison = case_when(comparison == "p.regimen.5.v.control" ~ "$\\theta_{5}$",
                                comparison == "p.regimen.4.v.control" ~ "$\\theta_{4}$",
                                comparison == "p.regimen.3.v.control" ~ "$\\theta_{3}$",
                                comparison == "p.regimen.2.v.control" ~ "$\\theta_{2}$")) %>% 
  ggplot(aes(y = comparison, x = posterior)) + 
  facet_wrap(~condition, ncol = 1) + 
  geom_point(position = position_jitter(width = 0, height = 0.35),
             aes(col = comparison),
             alpha = 0.5) +
  geom_boxplot(alpha = 0.3, # NEED TO INCORPORATE SAMPLE SIZE!!!
               width = 0.3,
               outlier.shape = NA,
               col = "white") +
  scale_color_manual(values = ucsf_col_pal) +
  scale_y_discrete(labels = TeX) +
  scale_x_continuous(TeX("$Pr_{\\theta}(\\theta > \\theta_1 | X)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  ggpubr::theme_pubr() +
  theme(legend.position = "none",
        axis.title.y = element_blank())

p30 + p40 + p60 + 
  plot_annotation(tag_levels = "A") 
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                       paste0(Sys.Date(), "_point-boxplot-posterior-comparison-v-control.png")),
       device = "png",
       height = 6,
       width = 10,
       units = "in")
```

```{r barplot-posterior-prob-top1, eval = FALSE}
even_stat <- ranking_probabilities$even_probabilities %>% 
  group_by(sim, nk) %>% 
  mutate(top = as.numeric(p.subset.1 == max(p.subset.1))) %>% 
  group_by(regimen, nk) %>% 
  summarise(n_top = sum(top)) %>% 
  mutate(condition = "Even")
hl_stat <- ranking_probabilities$highlow_probabilities %>% 
  group_by(sim, nk) %>% 
  mutate(top = as.numeric(p.subset.1 == max(p.subset.1))) %>% 
  group_by(regimen, nk) %>% 
  summarise(n_top = sum(top)) %>% 
  mutate(condition = "High-low")
high_stat <- ranking_probabilities$high_probabilities %>% 
  group_by(sim, nk) %>% 
  mutate(top = as.numeric(p.subset.1 == max(p.subset.1))) %>% 
  group_by(regimen, nk) %>% 
  summarise(n_top = sum(top)) %>% 
  mutate(condition = "High")

bind_rows(even_stat,
          hl_stat,
          high_stat) %>% 
  mutate(theta = paste0("$\\theta_{(", 6 - as.numeric(str_remove(regimen, "arm")), ")}$"),
         condition = factor(condition, levels = c("Even", "High-low", "High"))) %>%
  mutate(theta = factor(theta, levels = paste0("$\\theta_{(", 5:1, ")}$"))) %>% 
  ggplot(aes(x = nk, y = n_top, fill = theta)) + 
  facet_wrap(~condition, nrow = 1) +
  geom_area(position = "stack",
            alpha = 0.9) +
  scale_fill_manual(values = ucsf_col_pal[1:5], 
                    labels = TeX) +
  coord_cartesian(ylim = c(0,1000)) +
  scale_y_continuous(TeX("$p_3$"),
                     breaks = seq(0,1000,by = 200),
                     labels = seq(0,1,by = 0.2)) +
  scale_x_continuous(TeX("$n_k$")) +
  ggpubr::theme_pubr() +
  theme(legend.position = c(0.9,0.22),
        legend.title = element_blank(),
        legend.margin = margin(0,2,1,1),
        legend.direction = "vertical",
        axis.title.y = element_blank())

  # ggplot(aes(x = nk, y = n_top, fill = regimen)) + 
  # geom_bar(stat = "identity") +
  # scale_fill_manual("")
```

```{r}
p1 <- mutate(ranking_probabilities$even_probabilities, condition = "Even") %>% 
  filter(regimen %in% c("arm4", "arm5"),
         nk < 60) %>% 
  mutate(theta = paste0("$\\theta_{(", 6 - as.numeric(str_remove(regimen, "arm")), ")}$")) %>% 
  mutate(theta = factor(theta, levels = paste0("$\\theta_{(", 5:1, ")}$"))) %>% 
  group_by(regimen, nk) %>% 
  mutate(median = median(p.subset.1)) %>% 
  ggplot(aes(x = p.subset.1, fill = theta)) + 
  geom_density(alpha = 0.6,
               col = "white") + 
  geom_segment(aes(x = median, xend = median, y = 0, yend = 2.5, col = theta, lty = regimen)) +
  geom_point(aes(x = median, y = 0.1, bg = theta),
             shape = 24,
             size = 2,
             col = "white") +
  scale_fill_manual(values = ucsf_col_pal[1:5], 
                    labels = TeX) +
  scale_color_manual(values = ucsf_col_pal[1:5], 
                     labels = TeX) +
  scale_linetype_manual(values = c(2,3), 
                        labels = TeX,
                        guide = "none") +
  facet_wrap(~nk, ncol = 1) + 
  coord_cartesian(ylim = c(0,2.75)) +
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)}|X)$")) +
  ggpubr::theme_pubr() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none",
        legend.title = element_blank(),
        legend.margin = margin(0,2,1,1),
        legend.direction = "vertical",
        axis.title.y = element_blank())

p2 <- mutate(ranking_probabilities$highlow_probabilities, condition = "High-low") %>% 
  filter(regimen %in% c("arm4", "arm5"),
         nk < 60) %>% 
  mutate(theta = paste0("$\\theta_{(", 6 - as.numeric(str_remove(regimen, "arm")), ")}$")) %>% 
  mutate(theta = factor(theta, levels = paste0("$\\theta_{(", 5:1, ")}$"))) %>% 
  group_by(regimen, nk) %>% 
  mutate(median = median(p.subset.1)) %>% 
  ggplot(aes(x = p.subset.1, fill = theta)) + 
  geom_density(alpha = 0.6,
               col = "white") + 
  geom_segment(aes(x = median, xend = median, y = 0, yend = 2.5, col = theta, lty = theta)) +
  geom_point(aes(x = median, y = 0.1, bg = theta),
             shape = 24,
             size = 2,
             col = "white") +
  coord_cartesian(ylim = c(0,2.75)) +
  scale_fill_manual(values = ucsf_col_pal[1:5], 
                    labels = TeX) +
  scale_color_manual(values = ucsf_col_pal[1:5], 
                    labels = TeX) +
  scale_linetype_manual(values = c(2,3), 
                        labels = TeX,
                        guide = "none") +
  facet_wrap(~nk, ncol = 1) + 
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)}|X)$")) +
  ggpubr::theme_pubr() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none",
        legend.title = element_blank(),
        legend.margin = margin(0,2,1,1),
        legend.direction = "vertical",
        axis.title.y = element_blank())

p3 <- mutate(ranking_probabilities$high_probabilities, condition = "High") %>% 
  filter(regimen %in% c("arm4", "arm5"),
         nk < 60) %>% 
  mutate(theta = paste0("$\\theta_{(", 6 - as.numeric(str_remove(regimen, "arm")), ")}$")) %>% 
  mutate(theta = factor(theta, levels = paste0("$\\theta_{(", 5:1, ")}$"))) %>% 
  group_by(regimen, nk) %>% 
  mutate(median = median(p.subset.1)) %>% 
  ggplot(aes(x = p.subset.1, fill = theta)) + 
  geom_density(alpha = 0.6,
               col = "white") + 
  geom_segment(aes(x = median, xend = median, y = 0, yend = 2.5, col = theta, lty = theta)) +
  geom_point(aes(x = median, y = 0.1, bg = theta),
             shape = 24,
             col = "white") +
  scale_fill_manual(values = ucsf_col_pal[1:2],
                    labels = TeX) +
  scale_color_manual(values = ucsf_col_pal[1:5], 
                     labels = TeX,
                     # aesthetics = c("color", "bg", "fill")) +#,
                     guide = "none") +
  scale_linetype_manual(values = c(2,3), 
                        labels = TeX,
                        guide = "none") +
  coord_cartesian(ylim = c(0,2.75)) +
  facet_wrap(~nk, ncol = 1) + 
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)}|X)$")) +
  ggpubr::theme_pubr() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.9,0.15),
        legend.title = element_blank(),
        legend.margin = margin(0,2,1,1),
        legend.direction = "vertical",
        axis.title.y = element_blank())

p1 + p2 + p3 + 
  plot_annotation(tag_levels = "A") 
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope", 
                       paste0(Sys.Date(), "_density-plot_prob-steepest_top-2.png")),
       device = "png",
       width = 10,
       height = 5,
       units = "in")

ggsave(filename = here("graphs", "submission", "fig-05_density-plot_prob-steepest_top-2.tiff"),
       device = "tiff",
       width = 10,
       height = 5,
       units = "in")

p1 + p2 + p3 + 
  plot_annotation(tag_levels = "A",
                  title = "Dufault Fig. 5 (Top)") 

ggsave(filename = here("graphs", "submission", "fig-05_density-plot_prob-steepest_top-2_annotated.tiff"),
       device = "tiff",
       dpi = 600,
       width = 10,
       height = 5,
       units = "in")
```

#### $f(\psi_2)$: Comparing estimated confidence in top 2 regimens 

```{r boxplot-posterior-prob-top1}
ranking_probabilities$even_probabilities %>% 
  filter(regimen != "arm1") %>% 
  mutate(regimen.perc = case_when(regimen == "arm2" ~ "10%",
                                  regimen == "arm3" ~ "20%",
                                  regimen == "arm4" ~ "30%",
                                  regimen == "arm5" ~ "40%"),
         nk = as.factor(nk)) %>% 
  ggplot(aes(x = nk, y = p.subset.1)) +
  facet_wrap(~regimen.perc) +
  geom_violin(col = ucsf_col_pal[1],
              fill = ucsf_col_pal[1],
              width = 1,
              alpha = 0.3) +
  geom_boxplot(width = 0.1,
               outlier.shape = NA,
               fill = "white") +
  ylab(TeX("Pr$_{\\theta}(\\theta_{k} = \\theta_{(1)}$)")) + 
  xlab(TeX("Sample size per regimen, $n_k$")) + 
  ggpubr::theme_pubr()

p1 <- ranking_probabilities$even_probabilities %>% 
  ggplot(aes(x = p.subset.1, y = regimen, col = regimen, fill = regimen)) +
  facet_wrap(~nk, nrow = 1) +
  geom_boxplot(width = 0.6,
               alpha = 0.5) +
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)})$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_y_discrete("Slope, %", 
                   labels = c("Control", "10%", "20%", "30%", "40%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "none")  

p2 <- ranking_probabilities$highlow_probabilities %>% 
  ggplot(aes(x = p.subset.1, y = regimen, col = regimen, fill = regimen)) +
  facet_wrap(~nk, nrow = 1) +
  geom_boxplot(width = 0.6,
               alpha = 0.5) +
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)})$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_y_discrete("Slope, %", 
                   labels = c("Control", "-10%", "10%", "35%", "40%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "none")  

p3 <- ranking_probabilities$high_probabilities %>% 
  ggplot(aes(x = p.subset.1, y = regimen, col = regimen, fill = regimen)) +
  facet_wrap(~nk, nrow = 1) +
  geom_boxplot(width = 0.6,
               alpha = 0.5) +
  scale_x_continuous(TeX("$\\Pr_{\\theta}(\\theta_k = \\theta_{(1)})$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_y_discrete("Slope, %", 
                   labels = c("Control", "35%", "37%", "39%", "41%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  ggpubr::theme_pubr() + 
  theme(legend.position = "none")  

p1 / p2 / p3 +
  plot_annotation(tag_levels = "A") 
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope", 
                       paste0(Sys.Date(), "_boxplot-posterior-prob-top1.png")),
       device = "png",
       height = 6,
       width = 10,
       units = "in")
```

```{r}
p1 <- ranking_probabilities$even_probabilities %>% 
  filter(regimen %in% c("arm4", "arm5")) %>%  # Take the two true best arms
  dplyr::select(sim, regimen, p.subset.1, nk) %>% 
  pivot_wider(values_from = p.subset.1,
              names_from = regimen) %>% 
  mutate(p.diff = arm5 - arm4) %>% 
  ggplot(aes(x = as.factor(nk), y = p.diff)) + 
  geom_point(position = position_jitter(height = 0, width = 0.45),
             alpha = 0.1,
             aes(col = p.diff > 0)) + 
  scale_color_manual(values = ucsf_col_pal[3:4]) +
  geom_hline(yintercept = 0, 
             col= ucsf_col_pal[3],
             size = 1) + 
  geom_violin(width = 1,
              alpha = 0.6) +
  geom_boxplot(width = 0.05,
               outlier.shape = NA,
               fill = "darkgray",
               alpha = 0.5) +
  ggpubr::theme_pubr() +
  coord_cartesian(xlim = c(0,5)) + 
  ylab(TeX("$\\widehat{\\psi}_{2,(1)} - \\widehat{\\psi}_{2,(2)}$")) + 
  xlab(TeX("Sample size per regimen, $n_k$")) + 
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[4],
           hjust = 0,
           vjust = -0.5,
           label = "Favors true\nbest regimen") +
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[3],
           hjust = 0,
           vjust = 1.5,
           label = "Favors second\nbest regimen") + 
  theme(legend.position = "none",
        axis.title.x = element_blank())

p2 <- ranking_probabilities$highlow_probabilities %>% 
  filter(regimen %in% c("arm4", "arm5")) %>%  # Take the two true best arms
  dplyr::select(sim, regimen, p.subset.1, nk) %>% 
  pivot_wider(values_from = p.subset.1,
              names_from = regimen) %>% 
  mutate(p.diff = arm5 - arm4) %>% 
  ggplot(aes(x = as.factor(nk), y = p.diff)) + 
  geom_point(position = position_jitter(height = 0, width = 0.45),
             alpha = 0.1,
             aes(col = p.diff > 0)) + 
  scale_color_manual(values = ucsf_col_pal[3:4]) +
  geom_hline(yintercept = 0, 
             col= ucsf_col_pal[3],
             size = 1) + 
  geom_violin(width = 1,
              alpha = 0.6) +
  geom_boxplot(width = 0.05,
               outlier.shape = NA,
               fill = "darkgray",
               alpha = 0.5) +
  ggpubr::theme_pubr() +
  coord_cartesian(xlim = c(0,5)) + 
  ylab(TeX("$\\widehat{\\psi}_{2,(1)} - \\widehat{\\psi}_{2,(2)}$")) + 
  xlab(TeX("Sample size per regimen, $n_k$")) + 
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[4],
           hjust = 0,
           vjust = -0.5,
           label = "Favors true\nbest regimen") +
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[3],
           hjust = 0,
           vjust = 1.5,
           label = "Favors second\nbest regimen") + 
  theme(legend.position = "none")
  
p3 <- ranking_probabilities$high_probabilities %>% 
  filter(regimen %in% c("arm4", "arm5")) %>%  # Take the two true best arms
  dplyr::select(sim, regimen, p.subset.1, nk) %>% 
  pivot_wider(values_from = p.subset.1,
              names_from = regimen) %>% 
  mutate(p.diff = arm5 - arm4) %>% 
  ggplot(aes(x = as.factor(nk), y = p.diff)) + 
  geom_point(position = position_jitter(height = 0, width = 0.45),
             alpha = 0.1,
             aes(col = p.diff > 0)) + 
  scale_color_manual(values = ucsf_col_pal[3:4]) +
  geom_hline(yintercept = 0, 
             col= ucsf_col_pal[3],
             size = 1) + 
  geom_violin(width = 1,
              alpha = 0.6) +
  geom_boxplot(width = 0.05,
               outlier.shape = NA,
               fill = "darkgray",
               alpha = 0.5) +
  ggpubr::theme_pubr() +
  coord_cartesian(xlim = c(0,5)) + 
  ylab(TeX("$\\widehat{\\psi}_{2,(1)} - \\widehat{\\psi}_{2,(2)}$")) + 
  xlab(TeX("Sample size per regimen, $n_k$")) + 
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[4],
           hjust = 0,
           vjust = -0.5,
           label = "Favors true\nbest regimen") +
  annotate(geom = "text",
           x = -0.35, y = 0,
           col = ucsf_col_pal[3],
           hjust = 0,
           vjust = 1.5,
           label = "Favors second\nbest regimen") + 
  theme(legend.position = "none",
        axis.title.x = element_blank())


ggpubr::ggarrange(p1, p2, p3, ncol = 1,
                  labels = "AUTO")
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                       paste0(Sys.Date(), "_violin-box-point_posterior-comparison_best-v-second-best.png")),
       height = 10,
       width = 8,
       units = "in",
       device = "png"
)
```

#### $\psi_3$: Posterior probability of ranking in top 2 

```{r}
p1 <- ranking_probabilities$even_probabilities %>% 
  ggplot(aes(x = regimen, y = p.subset.2, col = regimen)) + 
  facet_wrap(~as.factor(nk), nrow = 1) + 
  geom_boxplot(aes(fill = regimen),
               alpha = 0.5,
               width = 0.6) + 
  scale_x_discrete("Slope, %",
                   labels = c("Control", "10%", "20%", "30%", "40%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  scale_y_continuous(TeX("P$\\left(\\theta \\in \\{\\theta_{(1)}, \\theta_{(2)}\\}\\right)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) + 
  ggpubr::theme_pubr() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  coord_flip()

p2 <- ranking_probabilities$highlow_probabilities %>% 
  ggplot(aes(x = regimen, y = p.subset.2, col = regimen)) + 
  facet_wrap(~as.factor(nk), nrow = 1) + 
  geom_boxplot(aes(fill = regimen),
               alpha = 0.5,
               width = 0.6) + 
  scale_x_discrete("Slope, %",
                   labels = c("Control", "-10%", "10%", "35%", "40%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  scale_y_continuous(TeX("P$\\left(\\theta \\in \\{\\theta_{(1)}, \\theta_{(2)}\\}\\right)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) + 
  ggpubr::theme_pubr() +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) + 
  coord_flip()

p3 <- ranking_probabilities$high_probabilities %>% 
  ggplot(aes(x = regimen, y = p.subset.2, col = regimen)) + 
  facet_wrap(~as.factor(nk), nrow = 1) + 
  geom_boxplot(aes(fill = regimen),
               alpha = 0.5,
               width = 0.6) + 
  scale_x_discrete("Slope, %",
                   labels = c("Control", "35%", "37%", "39%", "41%")) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_fill_manual(values = ucsf_col_pal) +
  scale_y_continuous(TeX("$\\psi_3 = Pr_{\\theta}\\left(\\theta \\in \\{\\theta_{(1)}, \\theta_{(2)}\\}|X\\right)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) + 
  ggpubr::theme_pubr() +
  theme(legend.position = "none") +
  coord_flip()

p1 / p2 / p3 +
  plot_annotation(tag_levels = "A") 
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope", 
                       paste0(Sys.Date(), "_boxplot-posterior-prob-top2.png")),
       device = "png",
       height = 6,
       width = 10,
       units = "in")
```

```{r}
temp1 <- ranking_probabilities$even_probabilities %>% 
  group_by(sim, nk) %>% 
  summarise(n.greater.than = min(p.subset.2[regimen %in% c("arm5", "arm4")]) > max(p.subset.2[!regimen %in% c("arm5", "arm4")])) %>% 
  group_by(nk) %>% 
  summarise(p.greater.than = mean(n.greater.than)) %>%
  mutate(condition = "Even")

temp2 <- ranking_probabilities$high_probabilities %>% 
  group_by(sim, nk) %>% 
  summarise(n.greater.than = min(p.subset.2[regimen %in% c("arm5", "arm4")]) > max(p.subset.2[!regimen %in% c("arm5", "arm4")])) %>% 
  group_by(nk) %>% 
  summarise(p.greater.than = mean(n.greater.than)) %>%
  mutate(condition = "High")

temp3 <- ranking_probabilities$highlow_probabilities %>% 
  group_by(sim, nk) %>% 
  summarise(n.greater.than = min(p.subset.2[regimen %in% c("arm5", "arm4")]) > max(p.subset.2[!regimen %in% c("arm5", "arm4")])) %>% 
  group_by(nk) %>% 
  summarise(p.greater.than = mean(n.greater.than)) %>%
  mutate(condition = "High-low")

p1 <- bind_rows(temp1, temp2, temp3) %>% 
  ggplot(aes(x = nk, y = p.greater.than, col = condition, lty = condition)) + 
  geom_line(size = 1) +
  scale_y_continuous(TeX("Pr\\left($\\min\\{\\psi_{3,(1)},\\psi_{3,(2)}\\}$ > $\\max\\{\\psi_{3,(3)},\\psi_{3,(4)},\\psi_{3,(5)}\\}\\right)$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_color_manual(values = ucsf_col_pal) +
  scale_x_continuous(TeX("$n_k$"))+
  ggpubr::theme_pubr() +
  coord_cartesian(ylim = c(0,1)) + 
  theme(legend.title = element_blank(),
        legend.position = c(0.92,0.15))

p1
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                       paste0(Sys.Date(), "_lineplot-psi3-vis.png")),
       device = "png",
       width = 5,
       height = 5,
       units = "in")
```

## Together

+ TTP (high-low) and Mixed survival rates such that:
  + Regimen 1 (control): 5% relapse rate, reference log10(TTP) slope
  + Regimen 2 (sub-optimal regimen): 10% relapse rate, -10% relative log10(TTP) slope
  + Regimen 3 (minimal regimen): 5% relapse rate, 10% relative log10(TTP) slope
  + Regimen 4 (minimal regimen): 5% relapse rate, 35% relative log10(TTP) slope
  + Regimen 5 (desirable regimen): 2.5% relapse rate, 40% relative log10(TTP) slope
  
### Stopping sub-optimal regimens

Stopping based on:    

+ TTP decision: NO-GO
+ P(rank in top 2) < 60%
+ Unfavorable Outcomes >= 2

```{r data-combined, eval = TRUE}
######################
# Regimen 2 (Sub-optimal)
######################
# relapses
out_hl_30_relapse_r1 <- s95.sit1.30 %>% # Situation 1: Regimen 2 - Sub-optimal
  filter(ttp.condition == "highlow", regimen == "2") %>%  # TTP did not play a role in simulating relapse data. Selection of ttp condition is irrelevant to the relapses counted. However, a unique relapse dataset was generated for each ttp condition so we will take advantage of this by pulling out the sub-optimal relapse counts from each dataset.
  dplyr::select(-regimen, -ttp.condition)
out_hl_30_relapse_r2 <- s95.sit1.30 %>% # Situation 1: Regimen 2 - Sub-optimal
  filter(ttp.condition == "high", regimen == "2") %>%  
  dplyr::select(-regimen, -ttp.condition)
out_hl_30_relapse_r3 <- s95.sit1.30 %>% # Situation 1: Regimen 2 - Sub-optimal
  filter(ttp.condition == "even", regimen == "2") %>% 
  dplyr::select(-regimen, -ttp.condition)
  
# TPP decision
out_hl_30_tpp_r1 <- decisions$decisions_highlow %>% # -10% slope
  filter(Regimen == "Regimen 1", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)
out_hl_30_tpp_r2 <- decisions$decisions_highlow %>% # 10% slope
  filter(Regimen == "Regimen 2", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)
out_hl_30_tpp_r3 <- decisions$decisions_even %>% # 20% slope
  filter(Regimen == "Regimen 2", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)

# Ranking
out_hl_30_ranking_r1 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm2") %>% # -10% slope
  dplyr::select(-regimen)
out_hl_30_ranking_r2 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm3") %>% # 10% slope
  dplyr::select(-regimen)
out_hl_30_ranking_r3 <- map_dfr(filter(ranking_probabilities$even_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm3") %>% #20% slope
  dplyr::select(-regimen)
  
out_hl_30_r1 <- full_join(
  full_join(out_hl_30_relapse_r1, out_hl_30_tpp_r1), 
                       out_hl_30_ranking_r1)
out_hl_30_r2 <- full_join(
  full_join(out_hl_30_relapse_r2, out_hl_30_tpp_r2), 
                       out_hl_30_ranking_r2)
out_hl_30_r3 <- full_join(
  full_join(out_hl_30_relapse_r3, out_hl_30_tpp_r3), 
                       out_hl_30_ranking_r3)
# Table(?)/Heatmap(?)
# focus in on sub-optimal regimens (relapse)
# sample size: 30
# panels: A) -10%, B) 10%, C) 20% slope
# prop stopped relapse, prop stopped TPP, prop not ranked first or second, prop stopped relapse | prop stopped TPP, prop stopped relapse | prop stopped TPP | not ranked first or second

t1 <- out_hl_30_r1 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6))) %>% 
  mutate(Slope = "-10%", .before = 1)

t2 <- out_hl_30_r2 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6))) %>% 
  mutate(Slope = "10%", .before = 1)

t3 <- out_hl_30_r3 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6))) %>% 
  mutate(Slope = "20%", .before = 1)

bind_rows(t1, t2, t3) %>% 
  kable(digits = 3) %>% 
  kable_styling()

p_df <- data.frame(relapse = ifelse(out_hl_30_r1$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                   TPP = ifelse(out_hl_30_r1$Decision == "NO-GO", "NO-GO", "Other"),
                   ranking = ifelse(out_hl_30_r1$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_2 <- data.frame(relapse = ifelse(out_hl_30_r2$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r2$Decision == "NO-GO", "NO-GO", "Other"),
                 ranking = ifelse(out_hl_30_r2$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_3 <- data.frame(relapse = ifelse(out_hl_30_r3$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r3$Decision == "NO-GO", "NO-GO", "Other"),
                 ranking = ifelse(out_hl_30_r3$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))


p1 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("-10% Relative Slope, TTP")

p2 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df_2$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df_2$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df_2$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df_2$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df_2$agree.relapse.TPP, 3)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df_2$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df_2$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_2$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("10% Relative Slope, TTP")

p3 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df_3$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df_3$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df_3$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df_3$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df_3$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df_3$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df_3$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_3$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("20% Relative Slope, TTP")

ggpubr::ggarrange(p1, p2, p3, nrow = 1)
# desirable regimens (relapse)
# prop stopped relapse, prop GO/Continue
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                              paste0(Sys.Date(), "_venn-diagram_all-together_sub-optimal-nk30.png")),
       height = 5,
       width = 12, 
       units = "in",
       device = "png")
```

### De-prioritizing sub-optimal regimens

De-prioritizing based on:    

+ TTP decision: NO-GO, **Continue**
+ P(rank in top 2) < 60%
+ Unfavorable Outcomes >= 2

```{r}
t1 <- out_hl_30_r1 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "-10%", .before = 1)

t2 <- out_hl_30_r2 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "10%", .before = 1)

t3 <- out_hl_30_r3 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "20%", .before = 1)

bind_rows(t1, t2, t3) %>% 
  kable(digits = 3) %>% 
  kable_styling()

p_df <- data.frame(relapse = ifelse(out_hl_30_r1$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                   TPP = ifelse(out_hl_30_r1$Decision == "GO", "Other", "NO-GO"),
                   ranking = ifelse(out_hl_30_r1$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_2 <- data.frame(relapse = ifelse(out_hl_30_r2$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r2$Decision == "GO", "Other", "NO-GO"),
                 ranking = ifelse(out_hl_30_r2$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_3 <- data.frame(relapse = ifelse(out_hl_30_r3$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r3$Decision == "GO", "Other", "NO-GO"),
                 ranking = ifelse(out_hl_30_r3$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))


p1 <- ggplot() + 
   # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("-10% Relative Slope, TTP")

p2 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df_2$only.relapse, 1), size = 6) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df_2$only.rank, 1), size = 6) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df_2$only.TPP, 1), size = 6) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df_2$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df_2$agree.relapse.TPP, 3)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df_2$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df_2$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_2$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("10% Relative Slope, TTP")

p3 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df_3$only.relapse, 1), size = 6) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df_3$only.rank, 1), size = 6) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df_3$only.TPP, 1), size = 6) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df_3$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df_3$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df_3$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df_3$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_3$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("20% Relative Slope, TTP")

p1 + p2 + p3 + 
  plot_annotation(tag_levels = "A")
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                              paste0(Sys.Date(), "_venn-diagram_all-together_sub-optimal-2-nk30.png")),
       height = 5,
       width = 12, 
       units = "in",
       device = "png")
```

### De-prioritizing sub-optimal regimens (NEW)

De-prioritizing based on:    

+ TTP decision: NO-GO, **Continue**
+ P(rank in top 2) < 60%
+ Unfavorable Outcomes >= 2

```{r}
######################
# Regimen 2 (Sub-optimal relapses)
######################
  
# TPP decision
out_hl_30_tpp_r1 <- decisions$decisions_highlow %>% # -10% slope
  filter(Regimen == "Regimen 1", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)
out_hl_30_tpp_r2 <- decisions$decisions_highlow %>% # 10% slope
  filter(Regimen == "Regimen 2", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)
out_hl_30_tpp_r3 <- decisions$decisions_highlow %>% # 35% slope
  filter(Regimen == "Regimen 3", nk == 30) %>% # indexing sets control at 0
  dplyr::select(-Regimen)

# Ranking
out_hl_30_ranking_r1 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm2") %>% # -10% slope
  dplyr::select(-regimen)
out_hl_30_ranking_r2 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm3") %>% # 10% slope
  dplyr::select(-regimen)
out_hl_30_ranking_r3 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm4") %>% # 35% slope
  dplyr::select(-regimen)
  
out_hl_30_r1 <- full_join(
  full_join(out_hl_30_relapse_r1, out_hl_30_tpp_r1), 
                       out_hl_30_ranking_r1)
out_hl_30_r2 <- full_join(
  full_join(out_hl_30_relapse_r2, out_hl_30_tpp_r2), 
                       out_hl_30_ranking_r2)
out_hl_30_r3 <- full_join(
  full_join(out_hl_30_relapse_r3, out_hl_30_tpp_r3), 
                       out_hl_30_ranking_r3)

t1 <- out_hl_30_r1 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "-10%", .before = 1)

t2 <- out_hl_30_r2 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "10%", .before = 1)

t3 <- out_hl_30_r3 %>% 
  summarise(`Stop relapse` = mean(n_relapse_interim1 >= 2),
            `Stop TPP` = mean(Decision == "NO-GO" | Decision == "Continue"),
            `P(top 2) < 0.6` = mean(p.subset.2 < 0.6),
            `Stop relapse or TPP` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | (Decision == "Continue")),
            `Stop relapse or TPP or P(top 2) < 0.6` = mean((n_relapse_interim1 >= 2) | (Decision == "NO-GO") | mean(p.subset.2 < 0.6) | (Decision == "Continue"))) %>% 
  mutate(Slope = "35%", .before = 1)

bind_rows(t1, t2, t3) %>% 
  kable(digits = 3) %>% 
  kable_styling()

p_df <- data.frame(relapse = ifelse(out_hl_30_r1$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                   TPP = ifelse(out_hl_30_r1$Decision == "GO", "Other", "NO-GO"),
                   ranking = ifelse(out_hl_30_r1$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_2 <- data.frame(relapse = ifelse(out_hl_30_r2$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r2$Decision == "GO", "Other", "NO-GO"),
                 ranking = ifelse(out_hl_30_r2$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_3 <- data.frame(relapse = ifelse(out_hl_30_r3$n_relapse_interim1 >= 2, "NO-GO", "Other"),
                 TPP = ifelse(out_hl_30_r3$Decision == "GO", "Other", "NO-GO"),
                 ranking = ifelse(out_hl_30_r3$p.subset.2 <= 0.6, "NO-GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "NO-GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "NO-GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "NO-GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "NO-GO")),
            only.relapse = mean((relapse == "NO-GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "NO-GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "NO-GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))

p1 <- ggplot() + 
   # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("-10% Relative Slope, TTP")

p2 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df_2$only.relapse, 1), size = 6) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df_2$only.rank, 1), size = 6) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df_2$only.TPP, 1), size = 6) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df_2$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df_2$agree.relapse.TPP, 3)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df_2$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df_2$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_2$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("10% Relative Slope, TTP")

p3 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 1.95+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable\n  Outcome", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 4.5, vjust = 1) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 4.5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.95, y = 2.25, label = round(100*p_df_3$only.relapse, 1), size = 6) +
  annotate(geom = "text", x = -0.95, y = 2.25, label = round(100*p_df_3$only.rank, 1), size = 6) +
  annotate(geom = "text", x = 0, y = 0.5, label = round(100*p_df_3$only.TPP, 1), size = 6) +
  annotate(geom = "text", x = -0.35, y = 1.325, hjust = 1, label = round(100*p_df_3$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.35, y = 1.325, hjust = 0, label = round(100*p_df_3$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.7, label = round(100*p_df_3$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.225, label = round(100*p_df_3$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Sub-optimal regimens missed: ", round(p_df_3$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("35% Relative Slope, TTP")

p1 + p2 + p3 + 
  plot_annotation(tag_levels = "A")
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                              paste0(Sys.Date(), "_venn-diagram_all-together_sub-optimal-3-nk30.png")),
       height = 5,
       width = 12, 
       units = "in",
       device = "png")

ggsave(filename = here("graphs", "submission",
                       "fig-06_venn-diagram_all-together_sub-optimal-3-nk30.tiff"),
       height = 5,
       width = 12, 
       units = "in",
       device = "tiff")

p1 + p2 + p3 + 
  plot_annotation(tag_levels = "A",
                  title = "Dufault Fig. 6 (Top)")

ggsave(filename = here("graphs", "submission",
                       "fig-06_venn-diagram_all-together_sub-optimal-3-nk30_annotated.tiff"),
       height = 5,
       dpi = 600,
       width = 12, 
       units = "in",
       device = "tiff")
```

### Desirable regimens

```{r data-combined-desirable, eval = TRUE}
######################
# Regimen 5 (Desirable)
######################
# Situation 2,(ALL Desirable) S(52) = .95
load(here("data","analyzed","2022-03-07_s95-situation2-results_nk30_4mo-duration.RData"))
s95.sit2.30 <- s95.situation2.results
load(here("data","analyzed","2022-03-07_s95-situation2-results_nk40_4mo-duration.RData"))
s95.sit2.40 <- s95.situation2.results
load(here("data","analyzed","2022-03-07_s95-situation2-results_nk60_4mo-duration.RData"))
s95.sit2.60 <- s95.situation2.results
load(here("data","analyzed","2022-03-07_s95-situation2-results_nk80_4mo-duration.RData"))
s95.sit2.80 <- s95.situation2.results; rm(s95.situation2.results)

# relapses
out_hl_30_relapse_r1 <- s95.sit2.30 %>% 
  filter(ttp.condition == "highlow", regimen == "1") %>%  # even though TTP did not play a role in simulating relapse data, a unique relapse dataset was simulated for each unique TTP data (essentially resulting in 3,000 simulated datasets of relapse for each regimen for each condition). 
  dplyr::select(-regimen)
out_hl_30_relapse_r2 <- s95.sit2.30 %>% 
  filter(ttp.condition == "even", regimen == "1") %>%  # even though TTP did not play a role in simulating relapse data, a unique relapse dataset was simulated for each unique TTP data (essentially resulting in 3,000 simulated datasets of relapse for each regimen for each condition). 
  dplyr::select(-regimen)
out_hl_30_relapse_r3 <- s95.sit1.30 %>% 
  filter(ttp.condition == "even", regimen == "2") %>% 
  dplyr::select(-regimen)
  
# TPP decision
out_hl_30_tpp_r1 <- decisions$decisions_highlow %>% 
  filter(Regimen == "Regimen 1", nk == 30) %>% # -10%
  dplyr::select(-Regimen)
out_hl_30_tpp_r2 <- decisions$decisions_even %>% 
  filter(Regimen == "Regimen 1", nk == 30) %>% # 10% 
  dplyr::select(-Regimen)
out_hl_30_tpp_r3 <- decisions$decisions_even %>% 
  filter(Regimen == "Regimen 2", nk == 30) %>% # 20%
  dplyr::select(-Regimen)

# Ranking
out_hl_30_ranking_r1 <- map_dfr(filter(ranking_probabilities$highlow_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm2") %>% 
  dplyr::select(-regimen)
out_hl_30_ranking_r2 <- map_dfr(filter(ranking_probabilities$even_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm2") %>% 
  dplyr::select(-regimen)
out_hl_30_ranking_r3 <- map_dfr(filter(ranking_probabilities$even_probabilities, nk == 30),
                             ~.x, .id = "sim") %>% 
  filter(regimen == "arm3") %>% 
  dplyr::select(-regimen)
  
out_hl_30_r1 <- full_join(
  full_join(out_hl_30_relapse_r1, out_hl_30_tpp_r1), 
                       out_hl_30_ranking_r1)
out_hl_30_r2 <- full_join(
  full_join(out_hl_30_relapse_r2, out_hl_30_tpp_r2), 
                       out_hl_30_ranking_r2)
out_hl_30_r3 <- full_join(
  full_join(out_hl_30_relapse_r3, out_hl_30_tpp_r3), 
                       out_hl_30_ranking_r3)
# Table(?)/Heatmap(?)
# focus in on sub-optimal regimens (relapse)
# sample size: 30
# panels: A) -10%, B) 10%, C) 20% slope
# prop stopped relapse, prop stopped TPP, prop not ranked first or second, prop stopped relapse | prop stopped TPP, prop stopped relapse | prop stopped TPP | not ranked first or second

t1 <- out_hl_30_r1 %>% 
  summarise(`GO relapse` = mean(n_relapse_interim1 < 2),
            `GO TPP` = mean(Decision == "GO"),
            `P(top 2) >= 0.6` = mean(p.subset.2 >= 0.6),
            `GO relapse and TPP` = mean((n_relapse_interim1 < 2) & (Decision == "GO")),
            `GO relapse and TPP and P(top 2) >= 0.6` = mean((n_relapse_interim1 < 2) & (Decision == "GO") & mean(p.subset.2 >= 0.6))) %>% 
  mutate(Slope = "-10%", .before = 1)

t2 <- out_hl_30_r2 %>% 
  summarise(`GO relapse` = mean(n_relapse_interim1 < 2),
            `GO TPP` = mean(Decision == "GO"),
            `P(top 2) >= 0.6` = mean(p.subset.2 >= 0.6),
            `GO relapse and TPP` = mean((n_relapse_interim1 < 2) & (Decision == "GO")),
            `GO relapse and TPP and P(top 2) >= 0.6` = mean((n_relapse_interim1 < 2) & (Decision == "GO") & mean(p.subset.2 >= 0.6))) %>%
  mutate(Slope = "10%", .before = 1)

t3 <- out_hl_30_r3 %>% 
  summarise(`GO relapse` = mean(n_relapse_interim1 < 2),
            `GO TPP` = mean(Decision == "GO"),
            `P(top 2) >= 0.6` = mean(p.subset.2 >= 0.6),
            `GO relapse and TPP` = mean((n_relapse_interim1 < 2) & (Decision == "GO")),
            `GO relapse and TPP and P(top 2) >= 0.6` = mean((n_relapse_interim1 < 2) & (Decision == "GO") & mean(p.subset.2 >= 0.6))) %>%
  mutate(Slope = "20%", .before = 1)

bind_rows(t1, t2, t3) %>% 
  kable(digits = 3) %>% 
  kable_styling()

p_df <- data.frame(relapse = ifelse(out_hl_30_r1$n_relapse_interim1 < 2, "GO", "Other"),
                   TPP = ifelse(out_hl_30_r1$Decision == "GO", "GO", "Other"),
                   ranking = ifelse(out_hl_30_r1$p.subset.2 >= 0.6, "GO", "Other")) %>% 
   summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "GO")),
            only.relapse = mean((relapse == "GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_2 <- data.frame(relapse = ifelse(out_hl_30_r2$n_relapse_interim1 < 2, "GO", "Other"),
                 TPP = ifelse(out_hl_30_r2$Decision == "GO", "GO", "Other"),
                 ranking = ifelse(out_hl_30_r2$p.subset.2 >= 0.6, "GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "GO")),
            only.relapse = mean((relapse == "GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))
p_df_3 <- data.frame(relapse = ifelse(out_hl_30_r3$n_relapse_interim1 < 2, "GO", "Other"),
                 TPP = ifelse(out_hl_30_r3$Decision == "GO", "GO", "Other"),
                 ranking = ifelse(out_hl_30_r3$p.subset.2 >= 0.6, "GO", "Other")) %>% 
  summarise(agree.relapse.rank = mean((relapse == ranking) & (relapse == "GO") & (TPP == "Other")),
            agree.relapse.TPP = mean((relapse == TPP) & (relapse == "GO") & (ranking == "Other")),
            agree.TPP.rank = mean((TPP == ranking) & (ranking == "GO") & (relapse == "Other")),
            agree.all = mean((TPP == ranking) & (TPP == relapse) & (relapse == "GO")),
            only.relapse = mean((relapse == "GO") & (TPP == "Other") & (ranking == "Other")),
            only.TPP = mean((TPP == "GO") & (ranking == "Other") & (relapse == "Other")),
            only.rank = mean((ranking == "GO") & (TPP == "Other") & (relapse == "Other")),
            p.missed = mean(relapse == "Other" & ranking == "Other" & TPP == "Other"))


p1 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Desirable regimens missed: ", round(p_df$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("-10% Relative Slope, TTP")

p2 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df_2$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df_2$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df_2$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df_2$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df_2$agree.relapse.TPP, 3)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df_2$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df_2$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Desirable regimens missed: ", round(p_df_2$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("10% Relative Slope, TTP")

p3 <- ggplot() + 
  # TPP
  geom_polygon(aes(x = 0+1*cos(seq(0,2*pi,length.out=100)), 
                   y = 1+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[1],
               alpha = 0.3) + 
  # Ranking
  geom_polygon(aes(x = -0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[2],
               alpha = 0.3) + 
  # Unfavorable Outcome
  geom_polygon(aes(x = 0.75+1*cos(seq(0,2*pi,length.out=100)),
                   y = 2.25+1*sin(seq(0,2*pi,length.out=100))),
               fill = ucsf_col_pal[3],
               alpha = 0.3) + 
  annotate(geom = "text", x = 1.5, y = 3, hjust = 0, label = "Unfavorable Outcome", size = 5) + 
  annotate(geom = "text", x = -1.5, y = 3, hjust = 1, label = "Ranking", size = 5) + 
  annotate(geom = "text", x = 0, y = 0, vjust = 1.1, label = "TPP", size = 5) + 
  coord_fixed(xlim = c(-3,3),
              ylim = c(-0.5, 3.5)) +
  annotate(geom = "text", x = 0.75, y = 2.25, label = round(100*p_df_3$only.relapse, 1), size = 5) +
  annotate(geom = "text", x = -0.75, y = 2.25, label = round(100*p_df_3$only.rank, 1), size = 5) +
  annotate(geom = "text", x = 0, y = 1, label = round(100*p_df_3$only.TPP, 1), size = 5) +
  annotate(geom = "text", x = -0.375, y = 1.55, hjust = 1, label = round(100*p_df_3$agree.TPP.rank, 1)) +
  annotate(geom = "text", x = 0.375, y = 1.55, hjust = 0, label = round(100*p_df_3$agree.relapse.TPP, 1)) +
  annotate(geom = "text", x = 0, y = 1.85, label = round(100*p_df_3$agree.all, 1)) +
  annotate(geom = "text", x = 0, y = 2.25, label = round(100*p_df_3$agree.relapse.rank, 1)) +
  ggpubr::theme_pubr() + 
  labs(caption = paste0("Desirable regimens missed: ", round(p_df_3$p.missed*100, 2), "%")) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("20% Relative Slope, TTP")

ggpubr::ggarrange(p1, p2, p3, nrow = 1)
# desirable regimens (relapse)
# prop stopped relapse, prop GO/Continue
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope",
                              paste0(Sys.Date(), "_venn-diagram_all-together_desirable-nk30.png")),
       height = 5,
       width = 12, 
       units = "in",
       device = "png")
```

## Single Example

```{r relapse-single}
df_relapse_single <- s95.sit1.30 %>% 
  filter(sim == 7, ttp.condition == "even")

t_relapse <- df_relapse_single  
```

```{r ttp-single}
df_single <- mcmc_mods_even_30[[7]] 

# turning estimates into relative, % slopes
df_single$arm2 <- (df_single$arm2 - df_single$arm1)/df_single$arm1
df_single$arm3 <- (df_single$arm3 - df_single$arm1)/df_single$arm1
df_single$arm4 <- (df_single$arm4 - df_single$arm1)/df_single$arm1
df_single$arm5 <- (df_single$arm5 - df_single$arm1)/df_single$arm1

t_estimates <- df_single[,2:5] %>% 
  pivot_longer(names_to = "regimen",
               values_to = "cred.est",
               cols = 1:4) %>% 
  group_by(regimen) %>% 
  summarise(est.median = quantile(cred.est, probs = 0.5),
            est.CI.l = quantile(cred.est, probs = 0.025),
            est.CI.u = quantile(cred.est, probs = 0.975)) 
```

```{r}
theta_lrv <- 0
theta_tv <- .2
tau_lrv <- 0.025
tau_tv <- 0.025

decision_function <- function(theta_lrv, theta_tv, tau_lrv, tau_tv, mcmc_chain){
  out <- mcmc_chain %>% 
    pivot_longer(names_to = "regimen",
                 values_to = "cred.est",
                 cols = everything()) %>% 
    group_by(regimen) %>% 
    summarise(est.CI.l = quantile(cred.est, probs = tau_lrv),
              est.CI.u = quantile(cred.est, probs = 1-tau_tv))
  
  output <- out %>% 
    mutate(decision = case_when(est.CI.u <= theta_tv ~ "NO-GO",
                                (est.CI.u > theta_tv & est.CI.l <= theta_lrv) ~ "Continue",
                                (est.CI.u > theta_tv & est.CI.l > theta_lrv) ~ "GO"))
  return(output)
}

t_tpp <- decision_function(theta_lrv = theta_lrv, theta_tv = theta_tv, tau_lrv = tau_lrv, tau_tv = tau_tv, mcmc_chain = df_single[,2:5]) 
```

```{r}
t_rank <- mcmc_rank_function(df_single) 
```

```{r}
t_gcontrol <- df_single[,2:5] %>% 
  pivot_longer(cols = everything(),
               names_to = "regimen", 
               values_to = "cred.est") %>% 
  group_by(regimen) %>% 
  summarise(p.greater.than.control = mean(cred.est > 0))  

```

```{r}
t_relapse %>% 
  mutate(regimen = paste0("arm", regimen)) %>% 
  full_join(t_estimates) %>% 
  full_join(t_tpp) %>% 
  full_join(t_gcontrol) %>% 
  full_join(t_rank) %>% 
  mutate(regimen = str_remove(regimen, "arm"),
         Duration = c(26,rep(16,4)),
         nk = 30) %>% 
  dplyr::select(Regimen = regimen, Duration = Duration, `No. patients` = nk, `No. relapses` = n_relapse_interim1, `$\\hat{\\theta}_{0.5}$` = est.median, `$\\hat{\\theta}_{0.025}$` = est.CI.l, `$\\hat{\\theta}_{0.975}$` = est.CI.u, `TPP decision` = decision, `$\\hat{\\psi}_1$` = p.greater.than.control, `$\\hat{\\psi}_2$` = p.subset.1, `$\\hat{\\psi}_3$` = p.subset.2) %>% 
  kable(digits = 3,
        caption = "Interim results from a single simulated phase 2B study with thirty partients per regimen. The target product profile (TPP) assumes $\\theta_{LRV} = 0, \\theta_{TV} = 20, \\tau_{LRV} = \\tau_{TV} = 0.025$.") %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 2, "Interim 1" = 9))
```

```{r eval = FALSE}
t_relapse %>% 
  mutate(regimen = paste0("arm", regimen)) %>% 
  full_join(t_estimates) %>% 
  full_join(t_tpp) %>% 
  full_join(t_gcontrol) %>% 
  full_join(t_rank) %>%
  ggplot()
```


## Frequentist summaries {.tabset .tabset-pills}

```{r}
# Even
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-20_even.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-30_even.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-40_even.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-60_even.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-80_even.RData"))

# High
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-20_high.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-30_high.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-40_high.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-60_high.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-80_high.RData"))

# High-Low
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-20_highlow.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-30_highlow.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-40_highlow.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-60_highlow.RData"))
load(here("data","cleaned","2022-06-27_summary_random-intercept-random-slope_nk-80_highlow.RData"))
```

```{r cache = TRUE, include=FALSE}
coef_rank_fn <- function(modresults){
  temp <- modresults$fixed[2:6,] %>% 
    rownames_to_column(var = "Regimen") %>% 
    mutate(Regimen = case_when(Regimen == "week" ~ "Regimen 1",
                               Regimen == "week:arm2" ~ "Regimen 2",
                               Regimen == "week:arm3" ~ "Regimen 3",
                               Regimen == "week:arm4" ~ "Regimen 4",
                               TRUE ~ "Regimen 5")) %>% 
    mutate("Slope" = ifelse(Regimen != "Regimen 1", 
                            Estimate + Estimate[Regimen == "Regimen 1"],
                            Estimate)) %>% 
    mutate(rank = rank(Slope)) # 5 is steepest
  
  output <- temp %>% 
    dplyr::select(Regimen, Slope, `l-95% CI`, rank)
  
  return(output)
}

plan(multisession)
rank20_even <- future_map_dfr(summary_mods_even_20, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank30_even <- future_map_dfr(summary_mods_even_30, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank40_even <- future_map_dfr(summary_mods_even_40, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank60_even <- future_map_dfr(summary_mods_even_60, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank80_even <- future_map_dfr(summary_mods_even_80, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)

rank20_high <- future_map_dfr(summary_mods_high_20, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank30_high <- future_map_dfr(summary_mods_high_30, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank40_high <- future_map_dfr(summary_mods_high_40, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank60_high <- future_map_dfr(summary_mods_high_60, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank80_high <- future_map_dfr(summary_mods_high_80, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)

rank20_highlow <- future_map_dfr(summary_mods_highlow_20, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank30_highlow <- future_map_dfr(summary_mods_highlow_30, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank40_highlow <- future_map_dfr(summary_mods_highlow_40, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank60_highlow <- future_map_dfr(summary_mods_highlow_60, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
rank80_highlow <- future_map_dfr(summary_mods_highlow_80, 
                              ~coef_rank_fn(.x), 
                              .id = "sim",
                              .progress = TRUE)
beepr::beep()
```

### P(top regimen has steepest estimated slope)

```{r fig.width = 13, fig.height = 5, fig.cap = "Frequentist summary of estimator performance across changes in sample size (nk) and differences in $\\log_{10}$(TTP) slope. For all panels, results are based on 1,000 simulated datasets were used for each sample size and condition. A) The proportion of simulations where a given arm was estimated to have the steepest slope. B) The proportion of simulations where the steepest estimated slope belonged to one of the true top two steepest arms. C) The proportion of simulations (y-axis) where the estimated 95\\% credible interval around the relative change in slope excludes zero (x-axis)."}

p1 <- bind_rows(mutate(filter(rank20_even, rank >= 4), nk = 20, condition = "1 Winner"),
                mutate(filter(rank30_even, rank >= 4), nk = 30, condition = "1 Winner"),
                mutate(filter(rank40_even, rank >= 4), nk = 40, condition = "1 Winner"),
                mutate(filter(rank60_even, rank >= 4), nk = 60, condition = "1 Winner"),
                mutate(filter(rank80_even, rank >= 4), nk = 80, condition = "1 Winner"),
                mutate(filter(rank20_high, rank >= 4), nk = 20, condition = "4 Winners"),
                mutate(filter(rank30_high, rank >= 4), nk = 30, condition = "4 Winners"),
                mutate(filter(rank40_high, rank >= 4), nk = 40, condition = "4 Winners"),
                mutate(filter(rank60_high, rank >= 4), nk = 60, condition = "4 Winners"),
                mutate(filter(rank80_high, rank >= 4), nk = 80, condition = "4 Winners"),
                mutate(filter(rank20_highlow, rank >= 4), nk = 20, condition = "2 Winners"),
                mutate(filter(rank30_highlow, rank >= 4), nk = 30, condition = "2 Winners"),
                mutate(filter(rank40_highlow, rank >= 4), nk = 40, condition = "2 Winners"),
                mutate(filter(rank60_highlow, rank >= 4), nk = 60, condition = "2 Winners"),
                mutate(filter(rank80_highlow, rank >= 4), nk = 80, condition = "2 Winners")) %>% 
  group_by(condition, nk, sim) %>% 
  summarise(p.true.present = max(Regimen == "Regimen 5")) %>% 
  group_by(condition, nk) %>% 
  summarise(p.true.present = mean(p.true.present)) %>% 
  mutate(condition = factor(condition, levels = c("1 Winner", "2 Winners", "4 Winners"))) %>% 
  ggplot(aes(x = nk, y = p.true.present, lty = condition, col = condition)) + 
  geom_hline(yintercept = 0.8,
             lty = 2,
             col = "darkgray") +
  geom_line(size = 1) +
  scale_color_manual(values = ucsf_col_pal) +
  coord_cartesian(ylim = c(0,1)) +
  scale_y_continuous(TeX("$p_1$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_x_continuous(TeX("$n_k$")) +
  ggpubr::theme_pubr() +
  theme(legend.position = c(0.85, 0.2),
        legend.title = element_blank(),
        axis.title.y = element_blank())

bind_rows(mutate(filter(rank20_even, rank >= 4), nk = 20, condition = "Even"),
          mutate(filter(rank30_even, rank >= 4), nk = 30, condition = "Even"),
          mutate(filter(rank40_even, rank >= 4), nk = 40, condition = "Even"),
          mutate(filter(rank60_even, rank >= 4), nk = 60, condition = "Even"),
          mutate(filter(rank80_even, rank >= 4), nk = 80, condition = "Even"),
          mutate(filter(rank20_high, rank >= 4), nk = 20, condition = "High"),
          mutate(filter(rank30_high, rank >= 4), nk = 30, condition = "High"),
          mutate(filter(rank40_high, rank >= 4), nk = 40, condition = "High"),
          mutate(filter(rank60_high, rank >= 4), nk = 60, condition = "High"),
          mutate(filter(rank80_high, rank >= 4), nk = 80, condition = "High"),
          mutate(filter(rank20_highlow, rank >= 4), nk = 20, condition = "High-low"),
          mutate(filter(rank30_highlow, rank >= 4), nk = 30, condition = "High-low"),
          mutate(filter(rank40_highlow, rank >= 4), nk = 40, condition = "High-low"),
          mutate(filter(rank60_highlow, rank >= 4), nk = 60, condition = "High-low"),
          mutate(filter(rank80_highlow, rank >= 4), nk = 80, condition = "High-low")) %>% 
  group_by(condition, nk, sim) %>% 
  summarise(p.true.present = max(Regimen == "Regimen 5")) %>% 
  group_by(condition, nk) %>% 
  summarise(p.true.present = mean(p.true.present)) %>% 
  kable(digits = 3) %>% 
  kable_styling()

p2 <- bind_rows(mutate(filter(rank20_even, rank == 5), nk = 20, condition = "Even"),
                mutate(filter(rank30_even, rank == 5), nk = 30, condition = "Even"),
                mutate(filter(rank40_even, rank == 5), nk = 40, condition = "Even"),
                mutate(filter(rank60_even, rank == 5), nk = 60, condition = "Even"),
                mutate(filter(rank80_even, rank == 5), nk = 80, condition = "Even"),
                mutate(filter(rank20_high, rank == 5), nk = 20, condition = "High"),
                mutate(filter(rank30_high, rank == 5), nk = 30, condition = "High"),
                mutate(filter(rank40_high, rank == 5), nk = 40, condition = "High"),
                mutate(filter(rank60_high, rank == 5), nk = 60, condition = "High"),
                mutate(filter(rank80_high, rank == 5), nk = 80, condition = "High"),
                mutate(filter(rank20_highlow, rank == 5), nk = 20, condition = "High-low"),
                mutate(filter(rank30_highlow, rank == 5), nk = 30, condition = "High-low"),
                mutate(filter(rank40_highlow, rank == 5), nk = 40, condition = "High-low"),
                mutate(filter(rank60_highlow, rank == 5), nk = 60, condition = "High-low"),
                mutate(filter(rank80_highlow, rank == 5), nk = 80, condition = "High-low")) %>% 
    mutate(condition = case_when(condition == "Even" ~ "1 Winner",
                               condition == "High" ~ "4 Winners",
                               TRUE ~ "2 Winners")) %>%
  group_by(condition, nk, Regimen) %>% 
  summarise(n = n()) %>% 
  group_by(condition, nk) %>% 
  summarise(prop = n/sum(n),
            Regimen) %>% #kable() %>% kable_styling()
  mutate(Regimen = factor(Regimen, levels = c(paste0("Regimen ", 1:5))),
         theta = paste0("$\\theta_{(", 6 - as.numeric(str_remove(Regimen, "Regimen ")), ")}$"),
         condition = factor(condition, levels = c("1 Winner", "2 Winners", "4 Winners"))) %>%
  mutate(theta = factor(theta, levels = paste0("$\\theta_{(", 5:1, ")}$"))) %>% 
  ggplot(aes(x = nk, y = prop, fill = theta)) + 
  facet_wrap(~condition) +
  geom_area(position = "stack") + #,
            # alpha = 0.9) +
  scale_fill_manual(values = ucsf_col_pal[1:5], 
                    labels = TeX) +
  coord_cartesian(ylim = c(0,1)) +
  scale_y_continuous(TeX("$p_3$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_x_continuous(TeX("$n_k$")) +
  ggpubr::theme_pubr() +
  theme(legend.position = c(0.9,0.22),
        legend.title = element_blank(),
        legend.margin = margin(0,2,1,1),
        legend.direction = "vertical",
        axis.title.y = element_blank())

bind_rows(mutate(filter(rank20_even, rank == 5), nk = 20, condition = "Even"),
                mutate(filter(rank30_even, rank == 5), nk = 30, condition = "Even"),
                mutate(filter(rank40_even, rank == 5), nk = 40, condition = "Even"),
                mutate(filter(rank60_even, rank == 5), nk = 60, condition = "Even"),
                mutate(filter(rank80_even, rank == 5), nk = 80, condition = "Even"),
                mutate(filter(rank20_high, rank == 5), nk = 20, condition = "High"),
                mutate(filter(rank30_high, rank == 5), nk = 30, condition = "High"),
                mutate(filter(rank40_high, rank == 5), nk = 40, condition = "High"),
                mutate(filter(rank60_high, rank == 5), nk = 60, condition = "High"),
                mutate(filter(rank80_high, rank == 5), nk = 80, condition = "High"),
                mutate(filter(rank20_highlow, rank == 5), nk = 20, condition = "High-low"),
                mutate(filter(rank30_highlow, rank == 5), nk = 30, condition = "High-low"),
                mutate(filter(rank40_highlow, rank == 5), nk = 40, condition = "High-low"),
                mutate(filter(rank60_highlow, rank == 5), nk = 60, condition = "High-low"),
                mutate(filter(rank80_highlow, rank == 5), nk = 80, condition = "High-low")) %>% 
  mutate(condition = case_when(condition == "Even" ~ "1 Winner",
                               condition == "High" ~ "4 Winners",
                               TRUE ~ "2 Winners")) %>%
  group_by(condition, nk, Regimen) %>% 
  summarise(n = n()) %>% 
  group_by(condition, nk) %>% 
  summarise(prop = n/sum(n),
            Regimen) %>%
  kable(digits = 3) %>% 
  kable_styling()

p3 <- bind_rows(mutate(rank20_even, nk = 20, condition = "Even"),
          mutate(rank30_even, nk = 30, condition = "Even"),
          mutate(rank40_even, nk = 40, condition = "Even"),
          mutate(rank60_even, nk = 60, condition = "Even"),
          mutate(rank80_even, nk = 80, condition = "Even"),
          mutate(rank20_high, nk = 20, condition = "High"),
          mutate(rank30_high, nk = 30, condition = "High"),
          mutate(rank40_high, nk = 40, condition = "High"),
          mutate(rank60_high, nk = 60, condition = "High"),
          mutate(rank80_high, nk = 80, condition = "High"),
          mutate(rank20_highlow, nk = 20, condition = "High-low"),
          mutate(rank30_highlow, nk = 30, condition = "High-low"),
          mutate(rank40_highlow, nk = 40, condition = "High-low"),
          mutate(rank60_highlow, nk = 60, condition = "High-low"),
          mutate(rank80_highlow, nk = 80, condition = "High-low")) %>% 
  filter((Regimen == "Regimen 2" & condition == "High-low") |
         (Regimen == "Regimen 2" & condition == "High") |
         (Regimen != "Regimen 1" & condition == "Even")) %>% 
  group_by(Regimen, nk, condition) %>% 
  mutate(neq.control = mean(`l-95% CI` > 0)) %>% 
  mutate(Slope = case_when(Regimen == "Regimen 2" & condition == "High-low" ~ "-10%",
                           Regimen == "Regimen 2" & condition == "High" ~ "35%",
                           Regimen == "Regimen 2" & condition == "Even" ~ "10%",
                           Regimen == "Regimen 3" & condition == "Even" ~ "20%",
                           Regimen == "Regimen 4" & condition == "Even" ~ "30%",
                           Regimen == "Regimen 5" & condition == "Even" ~ "40%")) %>% 
  mutate(Slope = factor(Slope, levels = c("-10%", "10%", "20%", "30%", "35%", "40%")),
         Slope.num = as.numeric(str_remove(Slope, "%"))) %>% 
  ggplot(aes(x = Slope.num, y = neq.control, col = as.factor(nk), lty = as.factor(nk))) + 
  geom_hline(yintercept = 0.8, lty = 2, col = "darkgray") +
  geom_line(aes(group = nk),
            size = 1) +
  scale_color_manual("nk", values = ucsf_col_pal) +
  scale_linetype_manual("nk", values = 1:5) +
  ggpubr::theme_pubr() + 
  scale_y_continuous(TeX("$p_6$"),
                     breaks = seq(0,1,by = 0.2),
                     labels = seq(0,1,by = 0.2)) +
  scale_x_continuous("Slope, %", 
                     breaks = seq(-10,40,by = 10),
                     labels = c("-10%", "0%", "10%", "20%", "30%", "40%")) +
  theme(legend.position = c(0.9,0.22),
        axis.title.y = element_blank(),
        legend.title = element_blank())
  
p2 + p1 + p3 + 
  plot_annotation(tag_levels = "A") 
```

```{r eval = FALSE}
ggsave(filename = here("graphs", "simulation-results", "random-intercept-random-slope", 
                       paste0(Sys.Date(), "_panel-plot-frequentist-summaries.png")),
       device = "png",
       width = 13,
       height = 5,
       units = "in")

ggsave(filename = here("graphs", "submission", "fig-02_panel-plot-frequentist-summaries.eps"),
       device = "eps",
       width = 13,
       height = 5,
       units = "in")
```

```{r eval = FALSE}
p2 + p1 + p3 + 
  plot_annotation(tag_levels = "A",
                  title = "Dufault Fig. 2 (Top)") 

ggsave(filename = here("graphs", "submission", "fig-02_panel-plot-frequentist-summaries_annotated.eps"),
       dpi = 600,
       device = "eps",
       width = 13,
       height = 5,
       units = "in")
```
